---
title: "R Notebook for Age Length Key Analysis"
output:
  rmarkdown::github_document: default
  html_document: default
  github_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)

```


### _Main Objectives of this script_
 1. Imports otolith data. Summarizes data, mean age, mean length, sd and se and total sample number.   
 2. Makes bay-specific observed ALK, calculates some summary statistics.  
 3. Makes bay specific smoothed (modeled) ALK with multinomial modeling methods in Ogle (87-).
 4. Likelihood ratio testing to do among group statistical comparisons - Ogle (102-103)
 5. Plots observed and smoothed ALK for each bay. 
 6. Calculates proportional age distribution
 7. Determines mean length -at-age (otolith database) and produces plots
 8. One way anova to determine if the mean lengths (and mean ages) of males and females are significantly different among estuaries
 9. T test to determine whether there is a significant difference between male and female age for each estuary
 10. T test to determine whether there is a significant difference in male and female length for each estuary.
11.Calculates proportional age distribution for ADULTS to be used in Delta_Method script (different from #6)
12. Calculates weight at age for ADULTS to be used in Delta_Method script

### _Start Here_ 
Load packages and set my working directory.
```{r warning=FALSE, message=FALSE}
library(FSA)
library(magrittr)
library(nnet)
library(plotrix)
library(haven)
library(ggplot2)
library(scales)
library(fishmethods) #masking select from dplyr 
library(dplyr)
library(gridExtra)
```

### 1. Load data and do some wrangling
 1. load the csv file
2. subset by which bay I want
3. subset the FIM program 
4. make sure I have just the "aged sample"
5. turn mm to cm
6. select just a few variables to make it more manageable
7. then drop the remaining bay levels still sticking around (droplevels)
8. turn tl from mm to cm
9. create length categories with FSA package

_Note: Because each dataset has its peculiarities I did this for each dataset and not within a loop or function_

```{r warning=FALSE, message=FALSE}
setwd("U:/PhD_projectfiles/Raw_Data/Age_Length_Data")
Agelength_TB<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_weight.csv", header=T)), bay=="TB" & tl>14 & final_age >0 & program== 'FIM', select=c(sex,SpecimenNumber, bay, tl,sl, final_age, wt_total, date, program))) %>% mutate(tl=tl/10, sl=sl/10, lcat2 =lencat(tl, w=2)) %>% filter(sex %in% c("m", "M", "F")) #, as.fact=TRUE))- can include this when determing ALK below but the smoothed ALK needs to be the nonfactored version of the length categorization variable. 
Agelength_TB$sex[which(Agelength_TB$sex == "m")] = "M"
Agelength_TB$sex <- droplevels(Agelength_TB$sex)

```


Change date format into a factor so that I can do summary statistics by year later on
```{r}
Agelength_TB$date=as.character(Agelength_TB$date)
Agelength_TB$DateNew = as.POSIXct(strptime(Agelength_TB$date, format="%d-%B-%y", tz=""))  #B is the selection for when month is spelled out
Agelength_TB = mutate(Agelength_TB, year = strftime(DateNew, format="%Y")) %>% dplyr::select(c(-date, -DateNew))
Agelength_TB$year = as.factor(Agelength_TB$year)

```
Now do the same thing for other estuaries. R code will not be displayed because it was fairly similar.

```{r echo=FALSE, warning=FALSE}
setwd("U:/PhD_projectfiles/Raw_Data/Age_Length_Data")
Agelength_AP<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_weight.csv", header=T)), bay=="AP" & tl>0 & final_age >0 & program== 'FIM', select=c(sex,SpecimenNumber, bay, tl,sl, final_age, wt_total, date, program))) %>% mutate(tl=tl/10, sl=sl/10, lcat2 =lencat(tl, w=2))%>% filter(sex %in% c("m", "M", "F")) #, as.fact=TRUE))

Agelength_AP$date=as.character(Agelength_AP$date)
Agelength_AP$DateNew = as.POSIXct(strptime(Agelength_AP$date, format="%d-%B-%y", tz="")) 
Agelength_AP = mutate(Agelength_AP, year = strftime(DateNew, format="%Y")) %>% dplyr::select(-date, -DateNew)
Agelength_AP$year = as.factor(Agelength_AP$year) 

Agelength_CK<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_weight.csv", header=T)), bay=="CK" & tl>0 & final_age >0 & program== 'FIM', select=c(sex,SpecimenNumber, bay, tl,sl, final_age, wt_total, date, program))) %>% mutate(tl=tl/10, sl=sl/10,lcat2 =lencat(tl, w=2)) %>% filter(sex %in% c("m", "M", "F")) # as.fact=TRUE))

Agelength_CK$date=as.character(Agelength_CK$date)
Agelength_CK$DateNew = as.POSIXct(strptime(Agelength_CK$date, format="%d-%B-%y", tz="")) 
Agelength_CK = mutate(Agelength_CK, year = strftime(DateNew, format="%Y")) %>% dplyr::select(-date, -DateNew)
Agelength_CK$year = as.factor(Agelength_CK$year) 

Agelength_CH<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_weight.csv", header=T)), bay=="CH" & tl>0 & final_age >0 & program== 'FIM', select=c(sex,SpecimenNumber, bay, tl,sl, final_age, wt_total, date, program))) %>% mutate(tl=tl/10,sl=sl/10, lcat2 =lencat(tl, w=2)) %>% filter(sex %in% c("m", "f", "M", "F"))# as.fact=TRUE))
Agelength_CH$sex[which(Agelength_CH$sex == "f")] = "F"
Agelength_CH$sex <- droplevels(Agelength_CH$sex)

Agelength_CH$date=as.character(Agelength_CH$date)
Agelength_CH$DateNew = as.POSIXct(strptime(Agelength_CH$date, format="%d-%B-%y", tz="")) 
Agelength_CH = mutate(Agelength_CH, year = strftime(DateNew, format="%Y")) %>% dplyr::select(-date, -DateNew)
Agelength_CH$year = as.factor(Agelength_CH$year) 

Agelength_IR<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_weight.csv", header=T)), bay=="IR" & tl>0 & final_age >0 & program== 'FIM', select=c(sex,SpecimenNumber, bay, tl,sl, final_age, wt_total, date, program))) %>% mutate(tl=tl/10,sl=sl/10, lcat2 =lencat(tl, w=2)) %>% filter(sex %in% c("m", "f", "M", "F")) # as.fact=TRUE))

Agelength_IR$date=as.character(Agelength_IR$date)
Agelength_IR$DateNew = as.POSIXct(strptime(Agelength_IR$date, format="%d-%B-%y", tz="")) 
Agelength_IR = mutate(Agelength_IR, year = strftime(DateNew, format="%Y")) %>% dplyr::select(-date, -DateNew)
Agelength_IR$year = as.factor(Agelength_IR$year) 

Agelength_JX<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_weight.csv", header=T)), bay=="JX" & tl>0 & final_age >0 & program== 'FIM', select=c(sex,SpecimenNumber, bay, tl,sl, final_age, wt_total, date, program))) %>% mutate(tl=tl/10,sl=sl/10, lcat2 =lencat(tl, w=2)) %>% filter(sex %in% c("m","f", "M", "F")) # as.fact=TRUE))

Agelength_JX$date=as.character(Agelength_JX$date)
Agelength_JX$DateNew = as.POSIXct(strptime(Agelength_JX$date, format="%d-%B-%y", tz="")) 
Agelength_JX = mutate(Agelength_JX, year = strftime(DateNew, format="%Y")) %>% dplyr::select(-date, -DateNew)
Agelength_JX$year = as.factor(Agelength_JX$year) 

```
### 2. Basic data summarization
```{r}
#total sample number of FIM data
All= rbind(Agelength_AP, Agelength_CK, Agelength_TB, Agelength_CH, Agelength_JX, Agelength_IR) #omits na
All <- na.omit(All)
```

```{r echo=FALSE}
#Age proportion under 3 years
All_3under = subset(All, final_age <=3)
Proprotion3under <- nrow(All_3under)/nrow(All)

#Min, max length
min(All$tl)
max(All$tl)

```

```{r}
#summarize the entire set and group by sex and then bay
Combined_sum <- dplyr::summarize(group_by(All, sex,bay), mean_tl=mean(tl), sd_tl=sd(tl), se_tl= sd_tl/(sqrt(length(final_age))),min_tl=min(tl), max_tl=max(tl), mean_age=mean(final_age), median_age=median(final_age),sd_age= sd(final_age), se_age=sd_age/sqrt(length(final_age)), min_age= min(final_age), max_age=max(final_age))

Combined_sum


```


Summarize each to get sex ratios etc. 

```{r}
#an example with Tampa Bay data
TB_sum <- summarise(Agelength_TB %>% filter(sex %in% c("M", "F")),mean_age=mean(final_age), median_age=median(final_age),sd_age= sd(final_age), se_age=sd_age/sqrt(length(final_age)), mean_tl = mean(tl), median_tl = median(tl), min_tl=min(tl), max_tl=max(tl), sd_tl= sd(tl), se_tl= sd_tl/(sqrt(length(final_age))), prop_F=nrow(subset(Agelength_TB, sex=="F"))/length(final_age),prop_M=nrow(subset(Agelength_TB, sex=="M"))/length(final_age), N_F=nrow(subset(Agelength_TB, sex=="F")), N_M=nrow(subset(Agelength_TB, sex=="M")), totN =N_F+N_M)
```
Now for all other estuaries but code not displayed. 

```{r echo=FALSE}
AP_sum <- summarise(Agelength_AP %>% filter(sex %in% c("M", "F")),mean_age=mean(final_age), median_age=median(final_age),sd_age= sd(final_age), se_age=sd_age/sqrt(length(final_age)), mean_tl = mean(tl), median_tl = median(tl),min_tl=min(tl), max_tl=max(tl), sd_tl= sd(tl), se_tl= sd_tl/(sqrt(length(final_age))), prop_F=nrow(subset(Agelength_AP, sex=="F"))/length(final_age),prop_M=nrow(subset(Agelength_AP, sex=="M"))/length(final_age), N_F=nrow(subset(Agelength_AP, sex=="F")), N_M=nrow(subset(Agelength_AP, sex=="M")), totN =N_F+N_M)
CH_sum <- summarise(droplevels(Agelength_CH %>% filter(sex %in% c("M", "F"))),mean_age=mean(final_age), median_age=median(final_age),sd_age= sd(final_age), se_age=sd_age/sqrt(length(final_age)), mean_tl = mean(tl), median_tl = median(tl),min_tl=min(tl), max_tl=max(tl), sd_tl= sd(tl), se_tl= sd_tl/(sqrt(length(final_age))), prop_F=nrow(subset(Agelength_CH, sex=="F"))/length(final_age),prop_M=nrow(subset(Agelength_CH, sex=="M"))/length(final_age), N_F=nrow(subset(Agelength_CH, sex=="F")), N_M=nrow(subset(Agelength_CH, sex=="M")), totN =N_F+N_M)

CK_sum <- summarise(Agelength_CK %>% filter(sex %in% c("M", "F")),mean_age=mean(final_age), median_age=median(final_age),sd_age= sd(final_age), se_age=sd_age/sqrt(length(final_age)), mean_tl = mean(tl), median_tl = median(tl),min_tl=min(tl), max_tl=max(tl), sd_tl= sd(tl), se_tl= sd_tl/(sqrt(length(final_age))), prop_F=nrow(subset(Agelength_CK, sex=="F"))/length(final_age),prop_M=nrow(subset(Agelength_CK, sex=="M"))/length(final_age), N_F=nrow(subset(Agelength_CK, sex=="F")), N_M=nrow(subset(Agelength_CK, sex=="M")), totN =N_F+N_M)
IR_sum <- summarise(Agelength_IR %>% filter(sex %in% c("M", "F")),mean_age=mean(final_age), median_age=median(final_age),sd_age= sd(final_age), se_age=sd_age/sqrt(length(final_age)), mean_tl = mean(tl), median_tl = median(tl),min_tl=min(tl), max_tl=max(tl), sd_tl= sd(tl), se_tl= sd_tl/(sqrt(length(final_age))), prop_F=nrow(subset(Agelength_IR, sex=="F"))/length(final_age),prop_M=nrow(subset(Agelength_IR, sex=="M"))/length(final_age), N_F=nrow(subset(Agelength_IR, sex=="F")), N_M=nrow(subset(Agelength_IR, sex=="M")), totN =N_F+N_M)
JX_sum <- summarise(Agelength_JX %>% filter(sex %in% c("M", "F")),mean_age=mean(final_age), median_age=median(final_age),sd_age= sd(final_age), se_age=sd_age/sqrt(length(final_age)), mean_tl = mean(tl), median_tl = median(tl),min_tl=min(tl), max_tl=max(tl), sd_tl= sd(tl), se_tl= sd_tl/(sqrt(length(final_age))), prop_F=nrow(subset(Agelength_JX, sex=="F"))/length(final_age),prop_M=nrow(subset(Agelength_JX, sex=="M"))/length(final_age), N_F=nrow(subset(Agelength_JX, sex=="F")), N_M=nrow(subset(Agelength_JX, sex=="M")), totN =N_F+N_M)
```
Add them together and make sure rownames are added
```{r}
All_sum <- rbind(AP_sum, CK_sum, TB_sum, CH_sum, JX_sum, IR_sum) 
rownames(All_sum) <- c("AP", "CK", "TB", "CH", "JX", "IR")
```


```{r echo=FALSE}
#limit minimum length to that in the recreational data set and THEN do summarization to compare. 

AL_TB <- subset(Agelength_TB, tl>24) 
AL_AP <- subset(Agelength_AP, tl>20)
AL_CH <- subset(Agelength_CH, tl>26)
AL_CK<- subset(Agelength_CK, tl>26)
AL_IR<- subset(Agelength_IR, tl>26)
AL_JX<- subset(Agelength_JX, tl>26)

AL_all <- rbind(AL_TB, AL_AP, AL_CH, AL_CK, AL_IR, AL_JX)
AL_sum <- AL_all %>% group_by(bay) %>% summarise(mean_age=mean(final_age), median_age=median(final_age),sd_age= sd(final_age), se_age=sd_age/sqrt(length(final_age)), mean_tl = mean(tl), median_tl = median(tl), min_tl=min(tl), max_tl=max(tl), sd_tl= sd(tl), se_tl= sd_tl/(sqrt(length(tl))))

```

### 3. Statistical analyses
Two way Anovas: To test for differences in age and length by bay and sex. 

```{r}
All_MF <- droplevels(subset(All, sex %in% c("M", "F")))

#differences in final age and length by estuary and sex
aov <- aov(final_age ~ sex + bay, data= All_MF)
summary(aov)
#Tukey's test for pairwise comparison
TukeyHSD(aov)


aov2 <- aov(tl ~ bay + sex, data= All_MF)
summary(aov2)
TukeyHSD(aov2)

#differences in final age and length by sex within each estuary
summary(aov(final_age ~  sex, data= AL_TB))
summary(aov(final_age ~  sex, data= AL_AP))
summary(aov(final_age ~  sex, data= AL_CK))
summary(aov(final_age ~  sex, data= AL_CH))
summary(aov(final_age ~  sex, data= AL_JX))
summary(aov(final_age ~  sex, data= AL_IR))

summary(aov(tl ~  sex, data= AL_TB))
summary(aov(tl  ~  sex, data= AL_AP))
summary(aov(tl  ~  sex, data= AL_CK))
summary(aov(tl  ~  sex, data= AL_CH))
summary(aov(tl  ~  sex, data= AL_JX))
summary(aov(tl  ~  sex, data= AL_IR))
```


#### Chi sqaured tests: To test differencs in age distribution between bays 
non-parameteric like anova is below so it doesnt assume normality of the age distribution  
can do a test of variance to determine whether can use anova  
anova assumes homogenous variances  
test for variances  
H0= ratio of variances is equal to 1   
Ha = ratio of variances is not equal to 1  

```{r warning=FALSE}
var.test(Agelength_TB$final_age, Agelength_AP$final_age) #equal variances
var.test(Agelength_TB$final_age, Agelength_CK$final_age)
var.test(Agelength_TB$final_age, Agelength_CH$final_age)
var.test(Agelength_TB$final_age, Agelength_IR$final_age) 
var.test(Agelength_TB$final_age, Agelength_JX$final_age)
var.test(Agelength_AP$final_age, Agelength_CK$final_age)
var.test(Agelength_AP$final_age, Agelength_CH$final_age) 
var.test(Agelength_AP$final_age, Agelength_IR$final_age)
var.test(Agelength_AP$final_age, Agelength_JX$final_age) #equal variances
var.test(Agelength_CK$final_age, Agelength_CH$final_age)
var.test(Agelength_CK$final_age, Agelength_IR$final_age)
var.test(Agelength_CK$final_age, Agelength_JX$final_age)
var.test(Agelength_CH$final_age, Agelength_IR$final_age)
var.test(Agelength_CH$final_age, Agelength_JX$final_age)
var.test(Agelength_IR$final_age, Agelength_JX$final_age)

#mostly all variances are unequal so use a chi squared test

#truncate to less than 8 to satisfy requirements of the test
ALL_to7 <- All %>% subset(final_age<8)
(age_freq <- xtabs(~bay+final_age, data=ALL_to7))

chisq.test(age_freq[1:2,]) 
chisq.test(age_freq[1:3,]) 
chisq.test(age_freq[1:4,]) 
chisq.test(age_freq[1:5,]) 
chisq.test(age_freq[1:6,]) 
chisq.test(age_freq[2:3,]) 
chisq.test(age_freq[2:4,]) 
chisq.test(age_freq[2:5,]) 
chisq.test(age_freq[2:6,]) 
chisq.test(age_freq[3:4,])
chisq.test(age_freq[3:5,]) 
chisq.test(age_freq[3:6,]) 
chisq.test(age_freq[4:5,]) 
chisq.test(age_freq[4:6,]) 
chisq.test(age_freq[5:6,]) 
```

```{r warning=FALSE}
#Adjusting p-values for the multople comparisons
ps_age<- c(chisq.test(age_freq[1:2,])$p.value,
           chisq.test(age_freq[1:3,])$p.value,
           chisq.test(age_freq[1:4,])$p.value,
           chisq.test(age_freq[1:5,])$p.value,
           chisq.test(age_freq[1:6,])$p.value,
           chisq.test(age_freq[2:3,])$p.value,
           chisq.test(age_freq[2:4,])$p.value,
           chisq.test(age_freq[2:5,])$p.value,
           chisq.test(age_freq[2:6,])$p.value,
           chisq.test(age_freq[3:4,])$p.value,
           chisq.test(age_freq[3:5,])$p.value,
           chisq.test(age_freq[3:6,])$p.value,
           chisq.test(age_freq[4:5,])$p.value,
           chisq.test(age_freq[4:6,])$p.value,
           chisq.test(age_freq[5:6,])$p.value)

pdf <- as.data.frame(p.adjust(ps_age))

#all significantly different excpet for TB to AP and CH and IR
```

#### Chi squared tests: to test for diferences in length distribution among areas
test for equal variances
```{r warning=FALSE}
var.test(Agelength_TB$tl, Agelength_AP$tl)
var.test(Agelength_TB$tl, Agelength_CK$tl)
var.test(Agelength_TB$tl, Agelength_CH$tl)
var.test(Agelength_TB$tl, Agelength_IR$tl) #equal variances
var.test(Agelength_TB$tl, Agelength_JX$tl)
var.test(Agelength_AP$tl, Agelength_CK$tl)
var.test(Agelength_AP$tl, Agelength_CH$tl) #equal variances
var.test(Agelength_AP$tl, Agelength_IR$tl)
var.test(Agelength_AP$tl, Agelength_JX$tl)
var.test(Agelength_CK$tl, Agelength_CH$tl)
var.test(Agelength_CK$tl, Agelength_IR$tl)
var.test(Agelength_CK$tl, Agelength_JX$tl)
var.test(Agelength_CH$tl, Agelength_IR$tl)
var.test(Agelength_CH$tl, Agelength_JX$tl)
var.test(Agelength_IR$tl, Agelength_JX$tl)

#unequal variances so will use chi.squared again

#truncate lengths to satisfy requirements
All_len_freq_30to58 <- All %>% subset(lcat2>=32 & lcat2<= 58)
(len_freq <- xtabs(~bay+lcat2, data=All_len_freq_30to58))

chisq.test(len_freq[1:2,]) 
chisq.test(len_freq[1:3,]) 
chisq.test(len_freq[1:4,]) 
chisq.test(len_freq[1:5,]) 
chisq.test(len_freq[1:6,]) 
chisq.test(len_freq[2:3,]) 
chisq.test(len_freq[2:4,]) 
chisq.test(len_freq[2:5,]) 
chisq.test(len_freq[2:6,]) 
chisq.test(len_freq[3:4,]) 
chisq.test(len_freq[3:5,]) 
chisq.test(len_freq[3:6,]) 
chisq.test(len_freq[4:5,]) 
chisq.test(len_freq[4:6,]) 
chisq.test(len_freq[5:6,]) 


ps_length <- c(chisq.test(len_freq[1:2,])$p.value, 
chisq.test(len_freq[1:3,])$p.value, 
chisq.test(len_freq[1:4,])$p.value, 
chisq.test(len_freq[1:5,])$p.value, 
chisq.test(len_freq[1:6,])$p.value, 
chisq.test(len_freq[2:3,])$p.value, 
chisq.test(len_freq[2:4,])$p.value, 
chisq.test(len_freq[2:5,])$p.value, 
chisq.test(len_freq[2:6,])$p.value, 
chisq.test(len_freq[3:4,])$p.value, 
chisq.test(len_freq[3:5,])$p.value, 
chisq.test(len_freq[3:6,])$p.value, 
chisq.test(len_freq[4:5,])$p.value, 
chisq.test(len_freq[4:6,])$p.value, 
chisq.test(len_freq[5:6,])$p.value) 

plength <- as.data.frame(p.adjust(ps_length))


```

### 4. Make age-length keys (ALKs) 
Make table with observed total numbers at length by age to be used for statistical analysis
```{r}
(rawfreq_TB <- xtabs(~lcat2+final_age, data=Agelength_TB)) 
#rawfreq_TB_test_df <- as.data.frame(as.matrix(xtabs(~lcat2+final_age, data=TB_test)))
# there appears to be a fish that was assigned an age of 3 but is in the 0-2 length category. Going to remove this because its probably a typo. Specified in above subsetting step as tl>20mm =(2cm).   
colSums(rawfreq_TB) #number of lengths obs per age
rowSums(rawfreq_TB) #number age obs per length
```
Now do for other estuaries
```{r echo=FALSE}
rawfreq_AP <- xtabs(~lcat2+final_age, data=Agelength_AP)
#rowSums(rawfreq_AP)
#colSums(rawfreq_AP)
rawfreq_CK <- xtabs(~lcat2+final_age, data=Agelength_CK) 
#rowSums(rawfreq_CK)
#colSums(rawfreq_CK)
rawfreq_CH <- xtabs(~lcat2+final_age, data=Agelength_CH) 
#rowSums(rawfreq_CH)
#colSums(rawfreq_CH)
rawfreq_IR <- xtabs(~lcat2+final_age, data=Agelength_IR) 
#rowSums(rawfreq_IR)
#colSums(rawfreq_IR)
rawfreq_JX <- xtabs(~lcat2+final_age, data=Agelength_JX)
#rowSums(rawfreq_JX)
#colSums(rawfreq_JX)

```

#### Make observed ALKs from tables produced above

The method to do so: 
The conditional proportions that form the ALK are calculated by dividing ecah cell of the frequency table by the sum of the corresponding row. 
These row proportions are constructed by submitting the xtabs() object to prop.table() and including margin=1 to indicate that the proportions are computed by row (page 92). 

The alkPlot command used for plotting the observed ALK is unable to extend the x axis to the bounds of c(0,80) because xlim is not working. 
 Therefore, in order to produce a plot with an x axis that can span from 0-80 (like what is happening with the length frequency and the smoothed ALK)
 I need to add in "observed" proportions for length categories that were not sampled. 
 I could have added them to the original data frame but I was concerned that in the process of proportion calculations the extra entries would
 affect the proportions or result in proportions that I didn't want. The smoothing process can estimate proportions outside of the range but I wanted 
 to keep the observed plot with just the proportions from the observed data. Therefore, I added in the zero proportion data by writing and editing
 a csv file which I then read below. 

```{r}
as.data.frame.matrix((prop.table(rawfreq_TB, margin=1))) %>% write.csv("U:/PhD_projectfiles/Exported_R_Datafiles/alk_TB.csv")
alk_TB <- read.csv("U:/PhD_projectfiles/Exported_R_Datafiles/alk_TB_edit.csv", row.names=1)
names(alk_TB) <- c(1,2,3,4,5,6,7,8,9)
round(alk_TB,3)

```
Now do the same with all of the others
```{r echo=FALSE}
as.data.frame.matrix((prop.table(rawfreq_CH, margin=1))) %>% write.csv("U:/PhD_projectfiles/Exported_R_Datafiles/alk_CH.csv")
alk_CH <- read.csv("U:/PhD_projectfiles/Exported_R_Datafiles/alk_CH_edit.csv", row.names=1)
names(alk_CH) <- c(1,2,3,4,5,6,7)
round(alk_CH,3)

as.data.frame.matrix((prop.table(rawfreq_CK, margin=1))) %>% write.csv("U:/PhD_projectfiles/Exported_R_Datafiles/alk_CK.csv")
alk_CK <- read.csv("U:/PhD_projectfiles/Exported_R_Datafiles/alk_CK_edit.csv", row.names=1)
names(alk_CK) <- c(1,2,3,4,5,6,7)
round(alk_CK,3)

as.data.frame.matrix((prop.table(rawfreq_AP, margin=1))) %>% write.csv("U:/PhD_projectfiles/Exported_R_Datafiles/alk_AP.csv")
alk_AP <- read.csv("U:/PhD_projectfiles/Exported_R_Datafiles/alk_AP_edit.csv", row.names=1)
names(alk_AP) <- c(1,2,3,4,5,6,7,8,9,10)
round(alk_AP,3)

as.data.frame.matrix((prop.table(rawfreq_JX, margin=1))) %>% write.csv("U:/PhD_projectfiles/Exported_R_Datafiles/alk_JX.csv")
alk_JX <- read.csv("U:/PhD_projectfiles/Exported_R_Datafiles/alk_JX_edit.csv", row.names=1)
names(alk_JX) <- c(1,2,3,4,5,6,7,8)
round(alk_JX,3)

as.data.frame.matrix((prop.table(rawfreq_IR, margin=1))) %>% write.csv("U:/PhD_projectfiles/Exported_R_Datafiles/alk_IR.csv")
alk_IR <- read.csv("U:/PhD_projectfiles/Exported_R_Datafiles/alk_IR_edit.csv", row.names=1)
names(alk_IR) <- c(1,2,3,4,5,6,7,8,9)
round(alk_IR,3)
```

#### Apply Proportional Age Distribution and Mean Length at Age
 1. Proportional age distribution  
 2. Mean length-at-age. (otolith database)

```{r}
#Proportional age distribution
  # might need to make sure I add some dummy data for bays that don't have equal number of ages
ad_TB <- xtabs(~final_age, data=Agelength_TB)
round(prop.table(ad_TB), 3)
```
Now do for other estuaries

```{r echo=FALSE}

ad_CK <- xtabs(~final_age, data=Agelength_CK)
round(prop.table(ad_CK), 3)

ad_CH <- xtabs(~final_age, data=Agelength_CH)
round(prop.table(ad_CH), 3)

ad_AP <- xtabs(~final_age, data=Agelength_AP)
round(prop.table(ad_AP), 3)

ad_IR <- xtabs(~final_age, data=Agelength_IR)
round(prop.table(ad_IR), 3)

ad_JX <- xtabs(~final_age, data=Agelength_JX)
round(prop.table(ad_JX), 3)
```

#### Summarize mean length-at-age for each area
```{r}
TB_sumlen <- Agelength_TB %>% group_by(final_age) %>% summarize(n=validn(tl), mn=mean(tl, na.rm=TRUE),
                                                    sd=sd(tl, na.rm=TRUE), se=se(tl, na.rm=TRUE)) %>%
                                                    as.data.frame()
```
Now do the rest of the estuaries
```{r echo=FALSE}
CK_sumlen <- Agelength_CK %>% group_by(final_age) %>% summarize(n=validn(tl), mn=mean(tl, na.rm=TRUE),
                                                    sd=sd(tl, na.rm=TRUE), se=se(tl, na.rm=TRUE)) %>%
                                                    as.data.frame()                                       

CH_sumlen <- Agelength_CH %>% group_by(final_age) %>% summarize(n=validn(tl), mn=mean(tl, na.rm=TRUE),
                                                    sd=sd(tl, na.rm=TRUE), se=se(tl, na.rm=TRUE)) %>%
                                                    as.data.frame()                                        
                                       
 AP_sumlen <- Agelength_AP %>% group_by(final_age) %>% summarize(n=validn(tl), mn=mean(tl, na.rm=TRUE),
                                                    sd=sd(tl, na.rm=TRUE), se=se(tl, na.rm=TRUE)) %>%
                                                    as.data.frame()
                                        
IR_sumlen <- Agelength_IR %>% group_by(final_age) %>% summarize(n=validn(tl), mn=mean(tl, na.rm=TRUE),
                                                   sd=sd(tl, na.rm=TRUE), se=se(tl, na.rm=TRUE)) %>%
                                                   as.data.frame() 
                                       
JX_sumlen <- Agelength_JX %>% group_by(final_age) %>% summarize(n=validn(tl), mn=mean(tl, na.rm=TRUE),
                                                  sd=sd(tl, na.rm=TRUE), se=se(tl, na.rm=TRUE)) %>%
                                                  as.data.frame()   

```

### 5. Visualize the data  
#### Make age histograms

```{r warning=FALSE}
age_AP <- ggplot(Agelength_AP, aes(x=final_age))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-0.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.4))+  ## plotting in percent frequency
  scale_x_continuous(name="Age (years)", limits=c(0,11), breaks=seq(1,10,1), labels=c(1,2,3,4,5,6,7,8,9,"10+"))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24, family="Times New Roman"), #changing  colour of x axisaxis.text.y=element_text(colour="black"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24, family="Times New Roman"), #changing colour of y acis
        axis.title.x=element_text(size=24, family="Times New Roman"),
        axis.title.y=element_text(size=24, family="Times New Roman"),
        plot.title=element_text(size=14))+
  annotate("text", x=10, y=.35, label="AP", size=10, family="Times New Roman")

age_AP
```
Now do the others

```{r echo=FALSE, warning=FALSE}

age_CK <- ggplot(Agelength_CK, aes(x=final_age))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.45))+  ## plotting in percent frequency
  scale_x_continuous(name="Age (years)", limits=c(0,11), breaks=seq(1,10,1), labels=c(1,2,3,4,5,6,7,8,9,"10+"))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24, family="Times New Roman"), #changing  colour of x axisaxis.text.y=element_text(colour="black"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24, family="Times New Roman"), #changing colour of y acis
        axis.title.x=element_text(size=24, family="Times New Roman"),
        axis.title.y=element_text(size=24, family="Times New Roman"),
        plot.title=element_text(size=14))+
  annotate("text", x=10, y=.35, label="CK", size=10, family="Times New Roman")

age_CK

age_TB <- ggplot(Agelength_TB, aes(x=final_age))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.4))+  ## plotting in percent frequency
  scale_x_continuous(name="Age (years)", limits=c(0,11), breaks=seq(1,10,1), labels=c(1,2,3,4,5,6,7,8,9,"10+"))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24, family="Times New Roman"), #changing  colour of x axisaxis.text.y=element_text(colour="black"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24, family="Times New Roman"), #changing colour of y acis
        axis.title.x=element_text(size=24, family="Times New Roman"),
        axis.title.y=element_text(size=24, family="Times New Roman"),
        plot.title=element_text(size=14))+
  annotate("text", x=10, y=.35, label="TB", size=10, family="Times New Roman")

age_TB

age_CH <- ggplot(Agelength_CH, aes(x=final_age))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.4))+  ## plotting in percent frequency
  scale_x_continuous(name="Age (years)", limits=c(0,11), breaks=seq(1,10,1), labels=c(1,2,3,4,5,6,7,8,9,"10+"))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24, family="Times New Roman"), #changing  colour of x axisaxis.text.y=element_text(colour="black"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24, family="Times New Roman"), #changing colour of y acis
        axis.title.x=element_text(size=24, family="Times New Roman"),
        axis.title.y=element_text(size=24, family="Times New Roman"),
        plot.title=element_text(size=14))+
  annotate("text", x=10, y=.35, label="CH", size=10, family="Times New Roman")
age_CH

age_JX <- ggplot(Agelength_JX, aes(x=final_age))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.45))+  ## plotting in percent frequency
  scale_x_continuous(name="Age (years)", limits=c(0,11), breaks=seq(1,10,1), labels=c(1,2,3,4,5,6,7,8,9,"10+"))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24, family="Times New Roman"), #changing  colour of x axisaxis.text.y=element_text(colour="black"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24, family="Times New Roman"), #changing colour of y acis
        axis.title.x=element_text(size=24, family="Times New Roman"),
        axis.title.y=element_text(size=24, family="Times New Roman"),
        plot.title=element_text(size=14))+
  annotate("text", x=10, y=.35, label="JX", size=10, family="Times New Roman")
age_JX
age_IR <- ggplot(Agelength_IR, aes(x=final_age))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.4))+  ## plotting in percent frequency
  scale_x_continuous(name="Age (years)", limits=c(0,11), breaks=seq(1,10,1), labels=c(1,2,3,4,5,6,7,8,9,"10+"))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24, family="Times New Roman"), #changing  colour of x axisaxis.text.y=element_text(colour="black"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24, family="Times New Roman"), #changing colour of y acis
        axis.title.x=element_text(size=24, family="Times New Roman"),
        axis.title.y=element_text(size=24, family="Times New Roman"),
        plot.title=element_text(size=14))+
  annotate("text", x=10, y=.35, label="IR", size=10, family="Times New Roman")

age_IR
```

```{r echo=FALSE}
#MULTIPLOT FUNCTION #####
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)
  
  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)
  
  numPlots = length(plots)
  
  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                     ncol = cols, nrow = ceiling(numPlots/cols))
  }
  
  if (numPlots==1) {
    print(plots[[1]])
    
  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    
    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}


#multiplot()
```
#### Length histograms. 

```{r warning =FALSE}
length_AP <- ggplot(Agelength_AP, aes(x=tl))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-0.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.10), breaks=seq(0,.10, .02))+  ## plotting in percent frequency
  scale_x_continuous(name="Length (cm)", limits=c(0,80), breaks=seq(0,80,20))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24, family="Times New Roman"), #changing  colour of x axisaxis.text.y=element_text(colour="black"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24, family="Times New Roman"), #changing colour of y acis
        axis.title.x=element_text(size=24, family="Times New Roman"),
        axis.title.y=element_text(size=24, family="Times New Roman"),
        plot.title=element_text(size=14))+
  annotate("text", x=65, y= .08, label="AP", size=10, family="Times New Roman")
length_AP
```
Now make plots for others. 

```{r echo=FALSE, warning=FALSE}
length_CK <- ggplot(Agelength_CK, aes(x=tl))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-0.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.10), breaks=seq(0,.10, .02))+  ## plotting in percent frequency
  scale_x_continuous(name="Length (cm)", limits=c(0,80), breaks=seq(0,80,20))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24, family="Times New Roman"), #changing  colour of x axisaxis.text.y=element_text(colour="black"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24, family="Times New Roman"), #changing colour of y acis
        axis.title.x=element_text(size=24, family="Times New Roman"),
        axis.title.y=element_text(size=24, family="Times New Roman"),
        plot.title=element_text(size=14))+
  annotate("text", x=65, y= .08, label="CK", size=10, family="Times New Roman")

length_CK

length_TB <- ggplot(Agelength_TB, aes(x=tl))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-0.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.10), breaks=seq(0,.10, .02))+  ## plotting in percent frequency
  scale_x_continuous(name="Length (cm)", limits=c(0,80), breaks=seq(0,80,20))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24, family="Times New Roman"), #changing  colour of x axisaxis.text.y=element_text(colour="blaTB"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24, family="Times New Roman"), #changing colour of y acis
        axis.title.x=element_text(size=24, family="Times New Roman"),
        axis.title.y=element_text(size=24, family="Times New Roman"),
        plot.title=element_text(size=14))+
  annotate("text", x=65, y= .08, label="TB", size=10, family="Times New Roman")
length_TB

length_CH <- ggplot(Agelength_CH, aes(x=tl))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-0.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.10), breaks=seq(0,.10, .02))+  ## plotting in percent frequency
  scale_x_continuous(name="Length (cm)", limits=c(0,80), breaks=seq(0,80,20))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24, family="Times New Roman"), #changing  colour of x axisaxis.text.y=element_text(colour="blaCH"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24, family="Times New Roman"), #changing colour of y acis
        axis.title.x=element_text(size=24, family="Times New Roman"),
        axis.title.y=element_text(size=24, family="Times New Roman"),
        plot.title=element_text(size=14))+
  annotate("text", x=65, y= .08, label="CH", size=10, family="Times New Roman")
length_CH
length_JX <- ggplot(Agelength_JX, aes(x=tl))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-0.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.10), breaks=seq(0,.10, .02))+  ## plotting in percent frequency
  scale_x_continuous(name="Length (cm)", limits=c(0,80), breaks=seq(0,80,20))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24, family="Times New Roman"), #JXanging  colour of x axisaxis.text.y=element_text(colour="blaJX"), #JXanging colour of y acis
        axis.text.y=element_text(colour="black", size=24, family="Times New Roman"), #JXanging colour of y acis
        axis.title.x=element_text(size=24, family="Times New Roman"),
        axis.title.y=element_text(size=24, family="Times New Roman"),
        plot.title=element_text(size=14))+
  annotate("text", x=65, y= .08, label="JX", size=10, family="Times New Roman")
length_JX

length_IR <- ggplot(Agelength_IR, aes(x=tl))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-0.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.10), breaks=seq(0,.10, .02))+  ## plotting in percent frequency
  scale_x_continuous(name="Length (cm)", limits=c(0,80), breaks=seq(0,80,20))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24, family="Times New Roman"), #IRanging  colour of x axisaxis.text.y=element_text(colour="blaIR"), #IRanging colour of y acis
        axis.text.y=element_text(colour="black", size=24, family="Times New Roman"), #IRanging colour of y acis
        axis.title.x=element_text(size=24, family="Times New Roman"),
        axis.title.y=element_text(size=24, family="Times New Roman"),
        plot.title=element_text(size=14))+
  annotate("text", x=65, y= .08, label="IR", size=10, family="Times New Roman")

length_IR
```

```{r}
#CROSSBAR PLOT for mean and standard error ####

MinMeanSEM196Max <- function(x) {
  v <- c(mean(x) - (sd(x)/sqrt(length(x))*1.96), mean(x), mean(x) + (sd(x)/sqrt(length(x))*1.96))
  names(v) <- c("ymin", "y", "ymax")
  v
}



All_min <- subset(All, sex %in% c("F", "M"))
labels <- c(F="Female", M="Male")

levels(All_min$bay) <- c("W1_AP", "W2_CK", "W3_TB", "W4_CH", "E1_JX", "E2_IR")

File <- ("U:/PhD_projectfiles/Figures/age_crossbar.tiff")
#if (file.exists(File)) stop(File, " already exists")
dir.create(dirname(File), showWarnings = FALSE)

tiff(File, units="in", width=5, height=7, res=300)

scaleFUN <- function(x) sprintf("%.1f", x)


#test <- All_min %>% group_by(bay) %>% summarize(n=length(final_age), mean_age=mean(final_age), UCI = mean_age + (sd(final_age)/sqrt(n)*1.96) , LCI = mean_age - (sd(final_age)/sqrt(n)*1.96))
#ggplot(test, aes(bay, mean_age)) + geom_crossbar(aes(ymin=LCI, ymax=UCI))

grid.arrange(ggplot(All_min %>% group_by(bay) %>% summarize(n=length(final_age), mean_age=mean(final_age), UCI = mean_age + (sd(final_age)/sqrt(n)*1.96) , LCI = mean_age - (sd(final_age)/sqrt(n)*1.96)), aes(bay, mean_age)) +
  stat_summary(fun.data=MinMeanSEM196Max, geom="crossbar", alpha=0.5) + #, colour="black") + 
  geom_crossbar(aes(ymin=LCI, ymax=UCI))+
  scale_y_continuous(limits=c(0,4), breaks=seq(0,5,0.5), labels=scaleFUN)+
  #facet_grid(sex ~., labeller=labeller(sex=labels)) +
  xlab("Estuary")+
  ylab("Age (yrs)")+
  theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank(), 									
        panel.background=element_rect(fill='white', colour='black'),
        axis.title.y = element_text(colour="black", size=18), # changing font of y axis title
        axis.title.x = element_blank(),
        axis.text.x=element_text(colour="black", size=12), #changing  colour and font of x axis text
        axis.text.y=element_text(colour="black", size=12),
        strip.text.y = element_text(size=16)) + 
  annotate("text", label= "a", x= 1, y = 2.8, size = 4) + 
annotate("text", label= "a", x= 3, y = 2.85, size = 4) +
  annotate("text", label= "a", x= 4, y = 2.79, size = 4) +
  annotate("text", label= "a", x= 6, y = 2.75, size = 4) +
  annotate("text", label= "b", x= 2, y = 2.22, size = 4) +
  annotate("text", label= "b", x= 5, y = 2.08, size = 4),
ggplot(All_min %>% group_by(bay,sex) %>% summarize(n=length(final_age), mean_age=mean(final_age), UCI = mean_age + (sd(final_age)/sqrt(n)*1.96) , LCI = mean_age - (sd(final_age)/sqrt(n)*1.96)), aes(bay, mean_age, fill=sex)) +
  geom_crossbar(aes(ymin=LCI, ymax=UCI), alpha=0.5)+
  scale_y_continuous(limits=c(0,4), breaks=seq(0,5,0.5), labels=scaleFUN)+
  #facet_grid(sex ~., labeller=labeller(sex=labels)) +
  xlab("Estuary")+
  ylab("Age (yrs)")+
  theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank(), 									
        panel.background=element_rect(fill='white', colour='black'),
        axis.title.y = element_text(colour="black", size=18), # changing font of y axis title
        axis.title.x = element_text(colour="black", size=18),
        axis.text.x=element_text(colour="black", size=12), #changing  colour and font of x axis text
        axis.text.y=element_text(colour="black", size=12),
        strip.text.y = element_text(size=16),
        legend.position= c(0.92,0.3), 
        legend.background= element_rect(color="black", linetype="solid"))  , nrow=2)

#changing colour and font of y axis
dev.off()

#plot.title=element_text(size=14), # changing size of plot title)



File <- ("U:/PhD_projectfiles/Figures/FIM_length_crossbar.tiff")
#if (file.exists(File)) stop(File, " already exists")
dir.create(dirname(File), showWarnings = FALSE)

tiff(File, units="in", width=5, height=7, res=300)

MinMedianSEM196Max <- function(x) {
  v <- c(median(x) - (sd(x)/sqrt(length(x))*1.96), median(x), median(x) + (sd(x)/sqrt(length(x))*1.96))
  names(v) <- c("ymin", "y", "ymax")
  v
}

#All_MF %>% group_by(bay, sex) %>% summarize(n=length(tl), mean_tl=mean(tl), UCI = mean_tl + (sd(tl)/sqrt(n)*1.96) , LCI = mean_tl - (sd(tl)/sqrt(n)*1.96))
#ggplot(test, aes(bay, mean_tl)) + geom_crossbar(aes(ymin=LCI, ymax=UCI))


scaleFUN <- function(x) sprintf("%.1f", x)
 grid.arrange(ggplot(All_min %>% group_by(bay) %>% summarize(n=length(tl), mean_tl=mean(tl), UCI = mean_tl + (sd(tl)/sqrt(n)*1.96) , LCI = mean_tl - (sd(tl)/sqrt(n)*1.96)), aes(bay, mean_tl)) +
  geom_crossbar(aes(ymin=LCI, ymax=UCI))+
  #scale_y_continuous(breaks=seq(10,80,1.5), labels=scaleFUN)+
    scale_y_continuous(limits=c(30,45), breaks=seq(30,45,2), labels=seq(30,45,2))+
  #facet_grid(sex ~., labeller=labeller(sex=labels)) +
  xlab("Estuary")+
  ylab("Total length (cm) ")+
  theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank(), 									
        panel.background=element_rect(fill='white', colour='black'),
        axis.title.y = element_text(colour="black", size=18), # changing font of y axis title
        axis.title.x = element_blank(),
        axis.text.x=element_text(colour="black", size=12), #changing  colour and font of x axis text
        axis.text.y=element_text(colour="black", size=12),
        strip.text.y = element_text(size=16))+
   annotate("text", label = "c", x=1, y= 41.05) +
   annotate("text", label = "d", x=2, y= 38.78) +
   annotate("text", label = "d", x=3, y= 39.08) +
   annotate("text", label = "d", x=4, y= 39.3) +
   annotate("text", label = "e", x=5, y= 35.19) +
   annotate("text", label = "d", x=6, y= 39.08),
 ggplot(All_min %>% group_by(bay, sex) %>% summarize(n=length(tl), mean_tl=mean(tl), UCI = mean_tl + (sd(tl)/sqrt(n)*1.96) , LCI = mean_tl - (sd(tl)/sqrt(n)*1.96)), aes(bay, mean_tl, fill=sex)) +
   stat_summary(fun.data=MinMeanSEM196Max, geom="crossbar", alpha=0.5) + #, colour="black") + 
   geom_crossbar(aes(ymin=LCI, ymax=UCI))+
   scale_y_continuous(limits=c(30,45), breaks=seq(30,45,2), labels=seq(30,45,2))+
   #facet_grid(sex ~., labeller=labeller(sex=labels)) +
   xlab("Estuary")+
   ylab("Total length (cm) ")+
   theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank(), 									
         panel.background=element_rect(fill='white', colour='black'),
         axis.title.y = element_text(colour="black", size=18), # changing font of y axis title
         axis.title.x = element_text(colour="black", size=18),
         axis.text.x=element_text(colour="black", size=12), #changing  colour and font of x axis text
         axis.text.y=element_text(colour="black", size=12),
         strip.text.y = element_text(size=16),
        legend.position= c(0.92,0.85), 
        legend.background= element_rect(color="black", linetype="solid")), nrow=2)
  
 #changing colour and font of y axis

#plot.title=element_text(size=14), # changing size of plot title)
dev.off()
```
```{r echo=FALSE}
### DISSERTATION PRESENTATION PLOTS ####
ggplot(All_min %>% group_by(bay) %>% summarize(n=length(tl), mean_tl=mean(tl), UCI = mean_tl + (sd(tl)/sqrt(n)*1.96) , LCI = mean_tl - (sd(tl)/sqrt(n)*1.96)), aes(bay, mean_tl)) +
  geom_crossbar(aes(ymin=LCI, ymax=UCI, color=bay))+
  scale_x_discrete(breaks=c("W1_AP", "W2_CK", "W3_TB", "W4_CH", "E1_JX", "E2_IR"), labels=c("AP", "CK", "TB", "CH", "JX", "IR"))+
  #scale_y_continuous(breaks=seq(10,80,1.5), labels=scaleFUN)+
  scale_y_continuous(limits=c(30,45), breaks=seq(30,45,2), labels=seq(30,45,2))+
  #facet_grid(sex ~., labeller=labeller(sex=labels)) +
  xlab("Area")+
  ylab("Total length (cm) ")+
  theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank(), 									
        panel.background=element_rect(fill='white', colour='black'),
        axis.title.y = element_text(colour="black", size=18), # changing font of y axis title
        axis.title.x = element_blank(),
        axis.text.x=element_text(colour="black", size=12), #changing  colour and font of x axis text
        axis.text.y=element_text(colour="black", size=12),
        strip.text.y = element_text(size=16),
        legend.position="none")


ggplot(All_min %>% group_by(bay) %>% summarize(n=length(final_age), mean_age=mean(final_age), UCI = mean_age + (sd(final_age)/sqrt(n)*1.96) , LCI = mean_age - (sd(final_age)/sqrt(n)*1.96)), aes(bay, mean_age)) +
  stat_summary(fun.data=MinMeanSEM196Max, geom="crossbar", alpha=0.5) + #, colour="black") + 
  geom_crossbar(aes(ymin=LCI, ymax=UCI, color=bay))+
  scale_x_discrete(breaks=c("W1_AP", "W2_CK", "W3_TB", "W4_CH", "E1_JX", "E2_IR"), labels=c("AP", "CK", "TB", "CH", "JX", "IR"))+
  scale_y_continuous(limits=c(0,4), breaks=seq(0,5,0.5), labels=scaleFUN)+
  #facet_grid(sex ~., labeller=labeller(sex=labels)) +
  xlab("Area")+
  ylab("Age (yrs)")+
  theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank(), 									
        panel.background=element_rect(fill='white', colour='black'),
        axis.title.y = element_text(colour="black", size=18), # changing font of y axis title
        axis.title.x = element_blank(),
        legend.position="none",
        axis.text.x=element_text(colour="black", size=12), #changing  colour and font of x axis text
        axis.text.y=element_text(colour="black", size=12),
        strip.text.y = element_text(size=16)) 
```
```{r echp=FALSE}
# PRODUCE SMOOTHED ALKS #####
#from multinomial modeling exercise which can be used to do Likelihood ratio testing. 
#MODELED AGE LENGTH KEYS (aka SMOOTHED ALK)
#-fixes two common issues with Age Length keys detailed on page 92 Ogle. 
#multinomial logistic regression model -Gerritsen et al. 2006. The response variable has more than two levels

#TB
tb <- multinom(final_age~lcat2, data=Agelength_TB, maxit=500)
lens<- seq(0,80, 1)
alksmo.tb <- predict(tb, data.frame(lcat2=lens), type="probs")
row.names(alksmo.tb) <- lens
round(alksmo.tb, 3)

#CK
ck <- multinom(final_age~lcat2, data=Agelength_CK, maxit=500)
lens<- seq(0,80, 1)
alksmo.ck <- predict(ck, data.frame(lcat2=lens), type="probs")
row.names(alksmo.ck) <- lens
round(alksmo.ck, 3)

#CH
ch <- multinom(final_age~lcat2, data=Agelength_CH, maxit=500)
lens<- seq(0,80, 1)
alksmo.ch <- predict(ch, data.frame(lcat2=lens), type="probs")
row.names(alksmo.ch) <- lens
round(alksmo.ch, 3)

#AP
ap <- multinom(final_age~lcat2, data=Agelength_AP, maxit=500)
lens<- seq(0,80, 1)
alksmo.ap <- predict(ap, data.frame(lcat2=lens), type="probs")
row.names(alksmo.ap) <- lens
round(alksmo.ap, 3)

#JX
jx <- multinom(final_age~lcat2, data=Agelength_JX, maxit=500)
lens<- seq(0,80, 1)
alksmo.jx <- predict(jx, data.frame(lcat2=lens), type="probs")
row.names(alksmo.jx) <- lens
round(alksmo.jx, 3)

#IR
ir <- multinom(final_age~lcat2, data=Agelength_IR, maxit=500)
lens<- seq(0,80, 1)
alksmo.ir <- predict(ir, data.frame(lcat2=lens), type="probs")
row.names(alksmo.ir) <- lens
round(alksmo.ir, 3)

```

```{r echo=FALSE, eval=FALSE}
#Plot length frequency by age, observed ALK, and modeled ALK #####
# Multiple options below. 


#Length frequency by age
histStack(lcat2~final_age, data=Agelength_TB, col=gray.colors(9, start=0, end=1), breaks=seq(0,80,1), xlim=c(0,80), ylim=c(0,700), xlab="Total Length (cm)", legend.pos="topright", xaxt="n") #remove col argument if we want it in rainbow format
axis(1, at=seq(0, 80, by=4))


histStack(lcat2~final_age, data=Agelength_CK, col=gray.colors(8, start=0, end=1), breaks=seq(0,80,1), ylim=c(0,80), xlab="Total Length (cm)", legend.pos="topright", xaxt="n") #remove col argument if we want it in rainbow format
axis(1, at=seq(0, 80, by=4))

histStack(lcat2~final_age, data=Agelength_CH, col=gray.colors(9, start=0, end=1), breaks=seq(0,80,1), ylim=c(0,250), xlab="Total Length (cm)", legend.pos="topright", xaxt="n") #remove col argument if we want it in rainbow format
axis(1, at=seq(0, 80, by=4))

histStack(lcat2~final_age, data=Agelength_AP, col=gray.colors(10, start=0, end=1), breaks=seq(0,80,1), ylim=c(0,350), xlab="Total Length (cm)", legend.pos="topright", xaxt="n") #remove col argument if we want it in rainbow format
axis(1, at=seq(0, 80, by=4))

histStack(lcat2~final_age, data=Agelength_IR, col=gray.colors(9, start=0, end=1), breaks=seq(0,80,1), ylim=c(0,500), xlab="Total Length (cm)", legend.pos="topright", xaxt="n") #remove col argument if we want it in rainbow format
axis(1, at=seq(0, 80, by=4))

histStack(lcat2~final_age, data=Agelength_JX, col=gray.colors(8, start=0, end=1), breaks=seq(0,80,1), ylim=c(0,100), xlab="Total Length (cm)", legend.pos="topright", xaxt="n") #remove col argument if we want it in rainbow format
axis(1, at=seq(0, 80, by=4))

####Observed ALK
alkPlot(alk_TB, type="barplot", xlab="Total Length (cm)", showLegend=T, pal="gray") #could remove legend and just reference in figure description

alkPlot(alk_CH, type="barplot", xlab="Total Length (cm)", showLegend=T, pal="gray")     

alkPlot(alk_CK, type="barplot", xlab="Total Length (cm)", showLegend=T, pal="gray")   

alkPlot(alk_AP, type="barplot", xlab="Total Length (cm)", showLegend=T, pal="gray")

alkPlot(alk_IR, type="barplot", xlab="Total Length (cm)", showLegend=T, pal="gray")

alkPlot(alk_JX, type="barplot", xlab="Total Length (cm)", showLegend=T, pal="gray")

 #Other options for plotting
     #obsTB <- alkPlot(alk_TB, type="area", pal="gray", showLegend=TRUE)
     #obsTB <- alkPlot(alk_TB, type="lines", showLegend=TRUE)
     #obsTB <- alkPlot(alk_TB, type="splines", showLegend=TRUE, span=0.1)


####Smoothed ALK####
smoTB <- alkPlot(alksmo.tb, type="barplot", xlab="Total Length (cm)", pal="rainbow", showLegend=TRUE)

smoCK <- alkPlot(alksmo.ck, type="barplot", xlab="Total Length (cm)", pal="rainbow", showLegend=TRUE)

smoCH <- alkPlot(alksmo.ch, type="barplot", xlab="Total Length (cm)", pal="rainbow", showLegend=TRUE)

smoAP <- alkPlot(alksmo.ap, type="barplot", xlab="Total Length (cm)", pal="rainbow", showLegend=TRUE)

smoIR <- alkPlot(alksmo.ir, type="barplot", xlab="Total Length (cm)", pal="rainbow", showLegend=TRUE)

smoJX <- alkPlot(alksmo.jx, type="barplot", xlab="Total Length (cm)", pal="rainbow", showLegend=TRUE)
```


### 6. Among group statistical comparisons of ALKs
#### Following methods on page 102 in Ogle, Fisheries Analysis in R
```{r}
setwd("U:/PhD_projectfiles/Raw_Data/Age_Length_Data")
Agelength_ALL<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "TB" | bay== "CK" | bay== "CH" | bay=="IR" |bay=="AP" | bay=="JX"),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_ALL, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_ALL, maxit=500) #more complex model

#likelihood ratio test is computed with anova
test <- anova(mod1, mod2)
# 1       lcat2    219195   66506.76                      
# 2 lcat2 * bay    219105   65007.89 1 vs 2    90 1498.865
# Pr(Chi)

#Drop Bays to test hypothesis of bay influence
      #Null Hypothesis- there is no significant difference in alk between groups

  #removing IR
Agelength_minIR<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "TB" | bay== "CK" | bay== "CH" | bay=="AP" | bay=="JX"),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_minIR, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_minIR, maxit=500) #more complex model

anova(mod1, mod2)
  #still significantly different

  #now remove JX also
Agelength_minIRJX<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "TB" | bay== "CK" | bay== "CH" | bay=="AP"),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_minIRJX, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_minIRJX, maxit=500) #more complex model

anova(mod1, mod2)
  #still significantly different

  #now remove AP also
Agelength_minIRJXAP<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "TB" | bay== "CK" | bay== "CH"),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_minIRJXAP, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_minIRJXAP, maxit=500) #more complex model

anova(mod1, mod2)

#now remove CH also
Agelength_minIRJXAPCH<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "TB" | bay== "CK"),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_minIRJXAPCH, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_minIRJXAPCH, maxit=500) #more complex model

anova(mod1, mod2)
  #still significantly different
```
#### Bay vs Bay comparison
Null Hypothesis- there is no significant difference in alk between groups

```{r}
#TB vs CK 
setwd("U:/PhD_projectfiles/Raw_Data/Age_Length_Data")
Agelength_TBCK<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "TB" |  bay== "CK" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_TBCK, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_TBCK, maxit=500) #more complex model

anova(mod1, mod2)
# The p value for testing the effect of the group in explaining the distribution of lengths within each age is obtained by computing a chi-square test-statistic
#Null Hypothesis- thre is no significant difference in alk between groups
# the likelihood ratio statistic is -2*LL (final value output) of model 1 MINUS
# -2*LL of model 2

#TB vs CH
Agelength_TBCH<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "TB" |  bay== "CH" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_TBCH, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_TBCH, maxit=500) #more complex model

anova(mod1, mod2)

#TB vs AP
Agelength_TBAP<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "TB" |  bay== "AP" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_TBAP, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_TBAP, maxit=500) #more complex model

anova(mod1, mod2)
#An alternative way to do a likelihood ratio test of nested models. 
library(lmtest)
#t <- lrtest(mod1, mod2)

#TB vs JX
Agelength_TBJX<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "TB" |  bay== "JX" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_TBJX, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_TBJX, maxit=500) #more complex model

anova(mod1, mod2)


#TB vs IR
Agelength_TBIR<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "TB" |  bay== "IR" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_TBIR, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_TBIR, maxit=500) #more complex model

anova(mod1, mod2)
```
Now do other comparisons

```{r echo=FALSE}
#CK vs CH
setwd("U:/PhD_projectfiles/Raw_Data/Age_Length_Data")
Agelength_CKCH<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "CK" |  bay== "CH" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_CKCH, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_CKCH, maxit=500) #more complex model

anova(mod1, mod2)

#CK Vs AP
Agelength_CKAP<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "CK" |  bay== "AP" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_CKAP, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_CKAP, maxit=500) #more complex model

anova(mod1, mod2)

#CK Vs JX
Agelength_CKJX<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "CK" |  bay== "JX" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_CKJX, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_CKJX, maxit=500) #more complex model

anova(mod1, mod2)

#CK Vs IR
Agelength_CKIR<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "CK" |  bay== "IR" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_CKIR, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_CKIR, maxit=500) #more complex model

anova(mod1, mod2)


#CH Vs AP
Agelength_CKAP<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "CH" |  bay== "AP" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_CKAP, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_CKAP, maxit=500) #more complex model

anova(mod1, mod2)

#CH Vs JX
Agelength_CKJX<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "CH" |  bay== "JX" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_CKJX, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_CKJX, maxit=500) #more complex model

anova(mod1, mod2)


#CH Vs IR
Agelength_CKIR<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "CH" |  bay== "IR" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_CKIR, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_CKIR, maxit=500) #more complex model

anova(mod1, mod2)

#AP Vs JX
Agelength_APJX<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "AP" |  bay== "JX" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_APJX, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_APJX, maxit=500) #more complex model

anova(mod1, mod2)


#AP Vs IR
Agelength_APIR<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "AP" |  bay== "IR" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_APIR, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_APIR, maxit=500) #more complex model

anova(mod1, mod2)

#JX Vs IR
Agelength_JXIR<- droplevels(subset(as.data.frame(read.csv("ALK_Bay_and_Weight.csv", header=T)),tl>20 & final_age >0 & (bay== "JX" |  bay== "IR" ),select=c(SpecimenNumber, bay, tl, final_age)) %>% mutate(tl=tl/10, lcat2 =lencat(tl, w=1))) # as.fact=TRUE))
mod1 <- multinom(final_age~lcat2, data=Agelength_JXIR, maxit=500) #simple model
mod2 <- multinom(final_age~lcat2*bay,data=Agelength_JXIR, maxit=500) #more complex model

anova(mod1, mod2)
```


```{r echo=FALSE, eval=FALSE}
#11. DETERMINE AGE PROPORTION OF ADULTS #####
#of all FIM subset... select sl > = 200 mm which is what was chosen to determine reproductively mature adults
# "Distribution of ages described by either the proportion of fish at age (Pi) or the number of fish at each age (Ni)" Ogle 96
"These calculcations are more easily performed by first computing the Nj values and then dividing each of these by N to compute the Pi values"


TB_adult <- subset(Agelength_TB, sl>= 20)
AP_adult <- subset(Agelength_AP, sl>=20)
CK_adult <- subset(Agelength_CK, sl>=20)
CH_adult <- subset(Agelength_CH, sl>=20)
JX_adult <- subset(Agelength_JX, sl>=20)
IR_adult <- subset(Agelength_IR, sl>=20)

age.n_TB <- xtabs(~final_age, data=TB_adult)
age.n_AP <- xtabs(~final_age, data=AP_adult)
age.n_CK <- xtabs(~final_age, data=CK_adult)
age.n_CH <- xtabs(~final_age, data=CH_adult)
age.n_JX <- xtabs(~final_age, data=JX_adult)
age.n_IR <- xtabs(~final_age, data=IR_adult)

#think I can use prop.table to give the proportion of fish at each age 

prop_TB <- as.data.frame(round(prop.table(age.n_TB),3))
prop_AP <- as.data.frame(round(prop.table(age.n_AP),3))
prop_CK <- as.data.frame(round(prop.table(age.n_CK),3))
prop_CH <- as.data.frame(round(prop.table(age.n_CH),3))
prop_JX <- as.data.frame(round(prop.table(age.n_JX),3))
prop_IR <- as.data.frame(round(prop.table(age.n_IR),3))

#Export proportions at adult age for the FIM catch to use in the Delta_Method script
#For personal computer
write.csv(prop_TB, "~/Desktop/PhD project/Projects/Seatrout/Data/Exported R Dataframes/PropAtAge_TBadult_FIMdata.csv")
write.csv(prop_AP, "~/Desktop/PhD project/Projects/Seatrout/Data/Exported R Dataframes/PropAtAge_APadult_FIMdata.csv")
write.csv(prop_CK, "~/Desktop/PhD project/Projects/Seatrout/Data/Exported R Dataframes/PropAtAge_CKadult_FIMdata.csv")
write.csv(prop_CH, "~/Desktop/PhD project/Projects/Seatrout/Data/Exported R Dataframes/PropAtAge_CHadult_FIMdata.csv")
write.csv(prop_JX, "~/Desktop/PhD project/Projects/Seatrout/Data/Exported R Dataframes/PropAtAge_JXadult_FIMdata.csv")
write.csv(prop_IR, "~/Desktop/PhD project/Projects/Seatrout/Data/Exported R Dataframes/PropAtAge_IRadult_FIMdata.csv")


#For work computer
write.csv(prop_TB, "U:/PhD_projectfiles/Exported_R_Datafiles/PropAtAge_TBadult_FIMdata.csv")
write.csv(prop_AP, "U:/PhD_projectfiles/Exported_R_Datafiles/PropAtAge_APadult_FIMdata.csv")
write.csv(prop_CK, "U:/PhD_projectfiles/Exported_R_Datafiles/PropAtAge_CKadult_FIMdata.csv")
write.csv(prop_CH, "U:/PhD_projectfiles/Exported_R_Datafiles/PropAtAge_CHadult_FIMdata.csv")
write.csv(prop_JX, "U:/PhD_projectfiles/Exported_R_Datafiles/PropAtAge_JXadult_FIMdata.csv")
write.csv(prop_IR, "U:/PhD_projectfiles/Exported_R_Datafiles/PropAtAge_IRadult_FIMdata.csv")

#12. DETERMINE WEIGHT AT AGE SCHEDULE OF ADULTS ######

Weight_at_Age_AP_ad <- Agelength_AP %>% group_by(final_age) %>% summarize(n=length(wt_total), mean_wt=mean(wt_total, na.rm=TRUE), sd=sd(wt_total, na.rm=TRUE), se=se(wt_total, na.rm=TRUE))
Weight_at_Age_CK_ad <- Agelength_CK %>% group_by(final_age) %>% summarize(n=length(wt_total), mean_wt=mean(wt_total, na.rm=TRUE), sd=sd(wt_total, na.rm=TRUE), se=se(wt_total, na.rm=TRUE))
Weight_at_Age_TB_ad <- Agelength_TB %>% group_by(final_age) %>% summarize(n=length(wt_total), mean_wt=mean(wt_total, na.rm=TRUE), sd=sd(wt_total, na.rm=TRUE), se=se(wt_total, na.rm=TRUE))
Weight_at_Age_CH_ad <- Agelength_CH %>% group_by(final_age) %>% summarize(n=length(wt_total), mean_wt=mean(wt_total, na.rm=TRUE), sd=sd(wt_total, na.rm=TRUE), se=se(wt_total, na.rm=TRUE))
Weight_at_Age_JX_ad <- Agelength_JX %>% group_by(final_age) %>% summarize(n=length(wt_total), mean_wt=mean(wt_total, na.rm=TRUE), sd=sd(wt_total, na.rm=TRUE), se=se(wt_total, na.rm=TRUE))
Weight_at_Age_IR_ad <- Agelength_IR %>% group_by(final_age) %>% summarize(n=length(wt_total), mean_wt=mean(wt_total, na.rm=TRUE), sd=sd(wt_total, na.rm=TRUE), se=se(wt_total, na.rm=TRUE))

#Export weight at adult age for the FIM catch to use in the Delta_Method script
#For personal computer
write.csv(Weight_at_Age_AP_ad, "~/Desktop/PhD project/Projects/Seatrout/Data/Exported R Dataframes/Weight_at_Age_APadult_FIMdata.csv")
write.csv(Weight_at_Age_CK_ad, "~/Desktop/PhD project/Projects/Seatrout/Data/Exported R Dataframes/Weight_at_Age_CKadult_FIMdata.csv")
write.csv(Weight_at_Age_TB_ad, "~/Desktop/PhD project/Projects/Seatrout/Data/Exported R Dataframes/Weight_at_Age_TBadult_FIMdata.csv")
write.csv(Weight_at_Age_CH_ad, "~/Desktop/PhD project/Projects/Seatrout/Data/Exported R Dataframes/Weight_at_Age_CHadult_FIMdata.csv")
write.csv(Weight_at_Age_JX_ad, "~/Desktop/PhD project/Projects/Seatrout/Data/Exported R Dataframes/Weight_at_Age_JXadult_FIMdata.csv")
write.csv(Weight_at_Age_IR_ad, "~/Desktop/PhD project/Projects/Seatrout/Data/Exported R Dataframes/Weight_at_Age_IRadult_FIMdata.csv")


#For work computer
write.csv(Weight_at_Age_AP_ad, "U:/PhD_projectfiles/Exported_R_Datafiles/Weight_at_Age_AP_ad_FIMdata.csv")
write.csv(Weight_at_Age_CK_ad, "U:/PhD_projectfiles/Exported_R_Datafiles/Weight_at_Age_CK_ad_FIMdata.csv")
write.csv(Weight_at_Age_TB_ad, "U:/PhD_projectfiles/Exported_R_Datafiles/Weight_at_Age_TB_ad_FIMdata.csv")
write.csv(Weight_at_Age_CH_ad, "U:/PhD_projectfiles/Exported_R_Datafiles/Weight_at_Age_CH_ad_FIMdata.csv")
write.csv(Weight_at_Age_JX_ad, "U:/PhD_projectfiles/Exported_R_Datafiles/Weight_at_Age_JX_ad_FIMdata.csv")
write.csv(Weight_at_Age_IR_ad, "U:/PhD_projectfiles/Exported_R_Datafiles/Weight_at_Age_IR_ad_FIMdata.csv")

```


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
