---
title: "R Notebook:Medoid_GC_NLSfit_plot.R"
output:
  github_document: 
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)

```


### _Main Objectives of this script_ 
 1. Determining medoids of each estuary so they can be used as great circle (GC) distance references
 2. ESTIMATE SPATIAL DECAY WITH NLS MODEL for both recruitment indices and RESIDUALS
 3. Determines lats and longs for adult data as well. 
 4. Produces a CSV file with all of the lats and longs


### _Start Here_ 
Load packages.

```{r warning=FALSE, message=FALSE}
library(haven) #for loading SAS data
library(cluster) #for finding medoid
library(geosphere) # for calculating great circle distances between each medoid
library(ggplot2) #for plotting
library(nlstools) #for fitting nls models
library(tidyverse)
library(ggrepel)
```
### _1. Load data and do some wrangling_
```{r}
setwd("U:/PhD_projectfiles/Raw_Data/Seatrout_FIM_Data/FIMData")
ap = subset(read_sas("ap_yoy_cn_c.sas7bdat"), month %in% c(6,7,8,9,10,11))
apl = read_sas("ap_yoy_cn_l.sas7bdat")

ck = subset(read_sas("ck_yoy_cn_c.sas7bdat"),  month %in% c(5,6,7,8,9,10,11)) 
ckl = read_sas("ck_yoy_cn_l.sas7bdat")

ch = subset(read_sas("ch_yoy_cn_c.sas7bdat"), month %in% c(4,5,6,7,8,9,10)) 
chl = read_sas("ch_yoy_cn_l.sas7bdat")

tb = subset(read_sas("tb_yoy_cn_c.sas7bdat"), month %in% c(4,5,6,7,8,9,10)) 
tbl = read_sas("tb_yoy_cn_l.sas7bdat")

ir = subset(read_sas("ir_yoy_cn_c.sas7bdat"), month %in% c(5,6,7,8,9,10,11)) 
irl = read_sas("ir_yoy_cn_l.sas7bdat")

jx = subset(read_sas("jx_yoy_cn_c.sas7bdat") , month %in% c(5,6,7,8,9,10,11))
jxl = read_sas("jx_yoy_cn_l.sas7bdat")


ap_all = ap
tb_all=tb
ch_all=ch
ck_all=ck
ir_all=ir
jx_all=jx
```

###_2.Medoid calculation_

```{r}
AP_LL <- subset(ap_all, select=c("Longitude", "Latitude")) 
  APMed <- pam(AP_LL,1)$medoids

```
Now do for remaining areas.
```{r include=FALSE}
CH_LL <- subset(ch_all, select=c("Longitude", "Latitude")) 
  CHMed <- pam(CH_LL,1)$medoids

CK_LL <- subset(ck_all, select=c("Longitude", "Latitude")) 
  CKMed <- pam(CK_LL,1)$medoids

IR_LL <-subset(ir_all, select=c("Longitude", "Latitude"))
  IRMed <- pam(IR_LL,1)$medoids

TB_LL <-na.omit(subset(tb_all, select=c("Longitude", "Latitude")))
  TBMed <- pam(TB_LL,1)$medoids

JX_LL <-subset(jx_all, select=c("Longitude", "Latitude"))
  JXMed <- pam(JX_LL,1)$medoids

```

### _3.Calculate great circle distance between pairs of areas_
```{r}
AP_compars = rbind(distGeo(APMed, CHMed, a=6378137, f=1/298.257223563),
                        distGeo(APMed, CKMed, a=6378137, f=1/298.257223563),
                        distGeo(APMed, TBMed, a=6378137, f=1/298.257223563),
                        distGeo(APMed, IRMed, a=6378137, f=1/298.257223563),
                        distGeo(APMed, JXMed, a=6378137, f=1/298.257223563))
```
Now do for other combinations
 
```{r include=FALSE}
CH_compars = rbind(distGeo(CHMed, CKMed, a=6378137, f=1/298.257223563),
                   distGeo(CHMed, TBMed, a=6378137, f=1/298.257223563),
                   distGeo(CHMed, IRMed, a=6378137, f=1/298.257223563),
                   distGeo(CHMed, JXMed, a=6378137, f=1/298.257223563))


CK_compars = rbind(distGeo(CKMed, TBMed, a=6378137, f=1/298.257223563),
                   distGeo(CKMed, IRMed, a=6378137, f=1/298.257223563),
                   distGeo(CKMed, JXMed, a=6378137, f=1/298.257223563))


TB_compars = rbind(distGeo(TBMed, IRMed, a=6378137, f=1/298.257223563),
                    distGeo(TBMed, JXMed, a=6378137, f=1/298.257223563))

IR_compars = distGeo(IRMed, JXMed, a=6378137, f=1/298.257223563)


```
####join distances together 
make sure they are in the correct order so that they can bind together with the csv imported below. 
```{r}
distances <- rbind(AP_compars, CH_compars, CK_compars, IR_compars, TB_compars)
rownames(distances) <- c("AP_CH", "AP_CK", "AP_TB", "AP_IR", "AP_JX", 
                         "CH_CK", "CH_TB", "CH_IR", "CH_JX",
                         "CK_TB", "CK_IR", "CK_JX",
                         "TB_IR", "TB_JX",
                         "IR_JX")
```

###_4.Combine mediods with rho values from spreadsheet_
```{r}
rho_P_vector <- read.csv('U:/PhD_projectfiles/Exported_R_Datafiles/rho_P_vector.csv', header=T)


#combine rho and distances vectors and then turn distance into kilometers, name x and y for plotting convention below
t<-cbind(rho_P_vector, distances) %>% mutate(distancesKM=distances/1000) %>% arrange(distancesKM) %>% rename(y=rho, x=distancesKM)
```

```{r eval=FALSE}
#export for later use
write.csv(t,'U:/PhD_projectfiles/Exported_R_Datafiles/rho_vs_distance.csv' )
```

```{r include=FALSE}
#r_min = r[-13,]  #testing out what happens if we remove the outlier that is CH-JX
```
###_5. Fit non linear square model to estimate spatial decay_
Two options:  
1. Fix p0= 1, just exclude it from the equation  
2. Estimate p0  
Pyper et al. 2001, Peterman et al. 1998  
P(d)= p0e(-d/v)- constrain p0 to 1  
P(d)=p0e(-d/v) - estimate P0  
v (e-folding scale) where e-folding scale tells distance   

```{r echo = FALSE}
setwd('U:/PhD_projectfiles/Exported_R_Datafiles')
t <- read.csv('U:/PhD_projectfiles/Exported_R_Datafiles/rho_vs_distance.csv', header=T)
```


must find acceptable starting values (can play around with these in excel-rho_vs_distance_param_start_estimation.csv)
```{r}
p0 = 1
v = 100
#p0 constrained to 1, weighted by the total sample number which is shared between each comparison
m1 = nls(y ~exp(-(x/v)), start=list(v=v), data=t, weights=(N))
overview(m1)
#estimated v 136.87(SE 26.66)
```
 p0 estimated
```{r warning=FALSE}
p0=0.9
v=125
m2 = nls(y ~p0*exp(-(x/v)), start=list(p0=p0,v=v), data=t, weights=(N))
summary(m2)
yfitted <- predict(m2)
boot <- nlsBoot(m2, niter=2000) #bootstrapping 
bootCI <- boot$bootCI #gives confidence intervals and median values for p0 and v (e-folding scale) where e-folding scale tells distance 
```
evalute fit with anova and F test. 
if they are significantly different than F test will indicated significant p value
```{r}
anova(m1, m2)
```
### _6. Visualize correlation by distance_ 

Plot correlation by distance and add the fitted curve to the plot(here p0 is estimated. see below for explanation)
http://stackoverflow.com/questions/25030653/fitting-with-ggplot2-geom-smooth-and-nls
 NOTE: within geom_smooth  it does not recognize variable names; they must be named x and y; weight must be in an aesthetic in ggplot

```{r include=FALSE}
t$y_short <- lapply(t$y, round, 2)
t$X <- as.character(t$X)

t <- t %>% separate(X, into =c("x1", "x2"), sep="_")
t[t == "AP"] <- "W1_AP"
t[t == "CK"] <- "W2_CK"
t[t == "TB"] <- "W3_TB"
t[t == "CH"] <- "W4_CH"
t[t == "JX"] <- "E1_JX"
t[t == "IR"] <- "E2_IR"

t_mut <- t %>% mutate(label=paste(x1, "v.", x2, y_short))
#trace(utils:::unpackPkgZip, edit=TRUE)
#require("ggrepel")
```

```{r eval=FALSE, echo=FALSE}
File <- ("U:/PhD_projectfiles/Figures/correlation_distance.tiff")
#if (file.exists(File)) stop(File, " already exists")
dir.create(dirname(File), showWarnings = FALSE)

tiff(File, units="in", width=8, height=6, res=300)
```

```{r}
ggplot(data=t_mut, aes(x=x, y=y, label = label))+geom_point()+ 
  geom_smooth(method="nls",formula=y ~exp(-(x/v)), method.args=list(start=c(v=150)), aes(weight=N), se=FALSE, color="black", size=1)+                                           
  ylab("Correlation") +
  xlab(" Great circle distance (km)")+ 
  geom_vline(xintercept = 128.46, linetype="dotted", size=1.5, color="red")+
  #geom_text(aes(label= label), vjust=1.5, hjust=0.5, size=2, check_overlap=T)+
  #geom_text_repel(aes(label=label), size=4)+
  geom_label_repel(aes(label=label))+
  #geom_label( check_overlap=T)+
  #geom_label(size=2.5, hjust = 1.1)+
  scale_x_continuous(limits=c(75,500))+
  #scale_y_continuous(limits=c(-0.3, 0.5, 0.1))+
  theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank(),  
        panel.background=element_rect(fill='white', colour='black'),                                                    
        axis.text.x=element_text(colour="black", size=14), #changing  colour of x axis
        axis.title.x=element_text(size=16),
        axis.title.y=element_text(size=16),
        axis.text.y=element_text(colour="black", size=14), #changing colour of y axis
        plot.title=element_text(size=14), # changing size of plot title)+
        legend.text=element_text(size=14))
```

```{r echo=FALSE}
dev.off()
```

