---
title: "R Notebook: Recreational_length_frequency_analysis"
output:
  github_document: 
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)

```
### _Main Objectives of this script_ 
 1. Imports mrfss and mrip length data.
 4. One way ANOVA to determine whether there is a significant difference in total length among estuaries
 2. Plots of ECDF
 3. Statistical comparison of bay-bay length frequencies. 
     - K-S test
     - Chi-Square Test


### _Start Here_ 
Load packages.
```{r warning=FALSE, message=FALSE}
library(FSA)
library(magrittr)
library(dplyr)
library(plotrix)
library(haven)
library(Matching)
library(dplyr)
library(ggplot2)
library(scales)
```

### _1. Load data and do some wrangling_
subset each estuary using the Country of Encounter codes
 From the definitions defined by FWRI
FIPS county codes


load data
select the counties that most closely align with the bays in question
 convert fork length to tl using the equation TLmm = 1.00467 * FL + 0.04850 from the SAS mrfss leng_freq
 chose data from 2000 on because of major regulatory changes 
```{r}
#setwd("~/Desktop/PhD project/Projects/Seatrout/Data")
setwd("U:/PhD_projectfiles/Raw_Data/Age_Length_Data")
mrfss <- read_sas("mrfss_lens_8115.sas7bdat")
mrip <- read_sas("mrip_lens_20042015.sas7bdat")

```

```{r}
setwd("U:/PhD_projectfiles/Raw_Data/Age_Length_Data")
mrfss_AP <- subset(read_sas("mrfss_lens_8115.sas7bdat"), CNTY %in% c(5,33,37,45,65,77,91,113,123,129,131,133) & YEAR>=2000 & YEAR <= 2003) %>% mutate(tl = (1.00467*flmm+0.04850)/10) %>% filter(!is.na(tl)) %>% mutate(bay=rep("AP",2234)) 
  mrfss_AP <- droplevels(subset(mrfss_AP, select=c(tl, bay)))
```
Now load other areas based on FIPS county designations
```{r include=FALSE}
setwd("U:/PhD_projectfiles/Raw_Data/Age_Length_Data")
mrfss_TB <- subset(read_sas("mrfss_lens_8115.sas7bdat"), CNTY %in% c(53,101,57,103,81) & YEAR>=2000 & YEAR<= 2003) %>% mutate(tl = (1.00467*flmm+0.04850)/10) %>% filter(!is.na(tl)) %>% mutate(bay=rep("TB",1741))
  mrfss_TB <- droplevels(subset(mrfss_TB, select=c(tl, bay)))
mrfss_CH <- subset(read_sas("mrfss_lens_8115.sas7bdat"), CNTY %in% c(27,115,7,15,71,21,87,51) & YEAR>=2000 & YEAR<= 2003) %>% mutate(tl = (1.00467*flmm+0.04850)/10) %>% filter(!is.na(tl))%>% mutate(bay=rep("CH",1085))
  mrfss_CH <- droplevels(subset(mrfss_CH, select=c(tl, bay)))
mrfss_CK <- subset(read_sas("mrfss_lens_8115.sas7bdat"), CNTY %in% c(75,29,17,1) & YEAR>=2000 & YEAR<= 2003) %>% mutate(tl = (1.00467*flmm+0.04850)/10) %>% filter(!is.na(tl))%>% mutate(bay=rep("CK",1225))
  mrfss_CK <- droplevels(subset(mrfss_CK, select=c(tl, bay)))
mrfss_JX <- subset(read_sas("mrfss_lens_8115.sas7bdat"), CNTY %in% c(19,31,35,89,107,109) & YEAR>=2000 & YEAR<= 2003) %>% mutate(tl = (1.00467*flmm+0.04850)/10) %>% filter(!is.na(tl))%>% mutate(bay=rep("JX",291))
  mrfss_JX <- droplevels(subset(mrfss_JX, select=c(tl, bay)))
mrfss_IR <- subset(read_sas("mrfss_lens_8115.sas7bdat"), CNTY %in% c(9,11,25,61,85,99,111,127) & YEAR>=2000 & YEAR <=2003) %>% mutate(tl = (1.00467*flmm+0.04850)/10) %>% filter(!is.na(tl))%>% mutate(bay=rep("IR",812))
  mrfss_IR <- droplevels(subset(mrfss_IR, select=c(tl, bay)))
```
Load the Mrip data as above. 

```{r include=FALSE}
setwd("U:/PhD_projectfiles/Raw_Data/Age_Length_Data")
mrip_AP <- subset(read_sas("mrip_lens_20042015.sas7bdat"), CNTY %in% c(5,33,37,45,65,77,91,113,123,129,131,133)) %>% mutate(tl = (1.00467*LNGTH+0.04850)/10) %>% filter(!is.na(tl)) %>% mutate(bay=rep("AP",9265))
  mrip_AP <- droplevels(subset(mrip_AP, select=c(tl, bay)))
```
Now the other areas

```{r include=FALSE}
setwd("U:/PhD_projectfiles/Raw_Data/Age_Length_Data")
mrip_TB <- subset(read_sas("mrip_lens_20042015.sas7bdat"), CNTY %in% c(53,101,57,103,81)) %>% mutate(tl = (1.00467*LNGTH+0.04850)/10) %>% filter(!is.na(tl)) %>% mutate(bay=rep("TB",8220))
  mrip_TB <- droplevels(subset(mrip_TB, select=c(tl, bay)))
mrip_CH <- subset(read_sas("mrip_lens_20042015.sas7bdat"), CNTY %in% c(27,115,7,15,71,21,87,51)) %>% mutate(tl = (1.00467*LNGTH+0.04850)/10) %>% filter(!is.na(tl))%>% mutate(bay=rep("CH",4832))
  mrip_CH <- droplevels(subset(mrip_CH, select=c(tl, bay)))
mrip_CK <- subset(read_sas("mrip_lens_20042015.sas7bdat"), CNTY %in% c(75,29,17,1)) %>% mutate(tl = (1.00467*LNGTH+0.04850)/10) %>% filter(!is.na(tl))%>% mutate(bay=rep("CK",5613))
  mrip_CK <- droplevels(subset(mrip_CK, select=c(tl, bay)))
mrip_JX <- subset(read_sas("mrip_lens_20042015.sas7bdat"), CNTY %in% c(19,31,35,89,107,109)) %>% mutate(tl = (1.00467*LNGTH+0.04850)/10) %>% filter(!is.na(tl))%>% mutate(bay=rep("JX",1510))
  mrip_JX <- droplevels(subset(mrip_JX, select=c(tl, bay)))
mrip_IR <- subset(read_sas("mrip_lens_20042015.sas7bdat"), CNTY %in% c(9,11,25,61,85,99,111,127)) %>% mutate(tl = (1.00467*LNGTH+0.04850)/10) %>% filter(!is.na(tl))%>% mutate(bay=rep("IR",2595))
  mrip_IR <- droplevels(subset(mrip_IR, select=c(tl, bay)))
```


combine data 
```{r}
AP <- rbind(mrfss_AP, mrip_AP)
TB <- rbind(mrfss_TB, mrip_TB)
CK <- rbind(mrfss_CK, mrip_CK)
CH <- rbind(mrfss_CH, mrip_CH)
JX <- rbind(mrfss_JX, mrip_JX)
IR <- rbind(mrfss_IR, mrip_IR)

All= rbind(AP, TB, CK, CH, JX, IR)
All$bay <- as.factor(All$bay)
All <- na.omit(All)
All$bay <- factor(All$bay, levels=c("AP", "CK", "TB", "CH", "JX", "IR"))

All_sum <- summarise(group_by(All, bay), N = length(tl), mean_tl = mean(tl), min_tl=min(tl), max_tl=max(tl), sd_tl= sd(tl), se_tl= sd_tl/(sqrt(length(tl))))
Rec_sum <- All_sum

N = nrow(AP) +nrow(TB) +nrow(CK) +nrow(CH) +nrow(JX) +nrow(IR)
```

### _2. Plot ecdf (empirical cumulative distribution function) - used for K-S test_

MRFSS
```{r echo=FALSE}
clr<- c("black", "gray50", "red", "blue", "green", "pink")
plot(ecdf(mrfss_TB$tl), xlab="Total Length (cm)", do.points=FALSE, verticals=TRUE, main="", col.01line=NULL)
plot(ecdf(mrfss_AP$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[2], col.01line=NULL)
plot(ecdf(mrfss_CK$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[3], col.01line=NULL)
plot(ecdf(mrfss_CH$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[4], col.01line=NULL)
plot(ecdf(mrfss_IR$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[5], col.01line=NULL)
plot(ecdf(mrfss_JX$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[6], col.01line=NULL)
```
MRIP
```{r echo=FALSE}
clr<- c("black", "gray50", "red", "blue", "green", "pink")
plot(ecdf(mrip_TB$tl), xlab="Total Length (cm)", do.points=FALSE, verticals=TRUE, main="", col.01line=NULL)
plot(ecdf(mrip_AP$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[2], col.01line=NULL)
plot(ecdf(mrip_CK$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[3], col.01line=NULL)
plot(ecdf(mrip_CH$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[4], col.01line=NULL)
plot(ecdf(mrip_IR$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[5], col.01line=NULL)
plot(ecdf(mrip_JX$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[6], col.01line=NULL)
```
ALL
```{r echo=FALSE}
clr<- c("black", "gray50", "red", "blue", "green", "pink")
plot(ecdf(TB$tl), xlab="Total Length (cm)", do.points=FALSE, verticals=TRUE, main="", col.01line=NULL)
plot(ecdf(AP$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[2], col.01line=NULL)
plot(ecdf(CK$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[3], col.01line=NULL)
plot(ecdf(CH$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[4], col.01line=NULL)
plot(ecdf(IR$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[5], col.01line=NULL)
plot(ecdf(JX$tl), add=TRUE, do.points=FALSE, verticals=TRUE, col=clr[6], col.01line=NULL)
```
test <- ecdf(TB$tl)
                                                               
### _3.Statistical comparisons to test length distributions_
####First with K-S Test 

used to determine whether ECDF are the same between two groups and can detect differences in location, dispersion and shape of the ditrubtions
bootstrapped version of the K-S test that is insensitive to ties with noncontinuous data is implemented in ks.boot
```{r}
ks<- c(ks.boot(mrfss_TB$tl, mrfss_CK$tl, nboots=1000)$p.value, ks.boot(mrfss_TB$tl, mrfss_CH$tl, nboots=5000)$p.value)
c <- ks.boot(mrfss_TB$tl, mrfss_TB$tl)
#if comparing more than two groups then each pair must be compared separately and the p value from each comparison must
# be adjusted for an increasing experimentwise error rate due to multiple comparisons. 
```
MRFSS
```{r}
ks_ALL_mrfss <-c(ks.boot(mrfss_TB$tl, mrfss_CK$tl, nboots=1000)$ks.boot.pvalue, 
  ks.boot(mrfss_TB$tl, mrfss_CH$tl, nboots=1000)$ks.boot.pvalue,
  ks.boot(mrfss_TB$tl, mrfss_AP$tl, nboots=1000)$ks.boot.pvalue,
  ks.boot(mrfss_TB$tl, mrfss_JX$tl, nboots=1000)$ks.boot.pvalue,
  ks.boot(mrfss_TB$tl, mrfss_IR$tl, nboots=1000)$ks.boot.pvalue,
  ks.boot(mrfss_CK$tl, mrfss_CH$tl, nboots=1000)$ks.boot.pvalue,
  ks.boot(mrfss_CK$tl, mrfss_AP$tl, nboots=1000)$ks.boot.pvalue,
  ks.boot(mrfss_CK$tl, mrfss_JX$tl, nboots=1000)$ks.boot.pvalue,
  ks.boot(mrfss_CK$tl, mrfss_IR$tl, nboots=1000)$ks.boot.pvalue,
  ks.boot(mrfss_CH$tl, mrfss_AP$tl, nboots=1000)$ks.boot.pvalue,
  ks.boot(mrfss_CH$tl, mrfss_JX$tl, nboots=1000)$ks.boot.pvalue,
  ks.boot(mrfss_CH$tl, mrfss_IR$tl, nboots=1000)$ks.boot.pvalue,
  ks.boot(mrfss_AP$tl, mrfss_JX$tl, nboots=1000)$ks.boot.pvalue,
  ks.boot(mrfss_AP$tl, mrfss_IR$tl, nboots=1000)$ks.boot.pvalue,
  ks.boot(mrfss_JX$tl, mrfss_IR$tl, nboots=1000)$ks.boot.pvalue)

p.adjust(ks_ALL_mrfss) 
```
MRIP
```{r}
ks_ALL_mrip <-c(ks.boot(mrip_TB$tl, mrip_CK$tl, nboots=1000)$ks.boot.pvalue, 
                 ks.boot(mrip_TB$tl, mrip_CH$tl, nboots=1000)$ks.boot.pvalue,
                 ks.boot(mrip_TB$tl, mrip_AP$tl, nboots=1000)$ks.boot.pvalue,
                 ks.boot(mrip_TB$tl, mrip_JX$tl, nboots=1000)$ks.boot.pvalue,
                 ks.boot(mrip_TB$tl, mrip_IR$tl, nboots=1000)$ks.boot.pvalue,
                 ks.boot(mrip_CK$tl, mrip_CH$tl, nboots=1000)$ks.boot.pvalue,
                 ks.boot(mrip_CK$tl, mrip_AP$tl, nboots=1000)$ks.boot.pvalue,
                 ks.boot(mrip_CK$tl, mrip_JX$tl, nboots=1000)$ks.boot.pvalue,
                 ks.boot(mrip_CK$tl, mrip_IR$tl, nboots=1000)$ks.boot.pvalue,
                 ks.boot(mrip_CH$tl, mrip_AP$tl, nboots=1000)$ks.boot.pvalue,
                 ks.boot(mrip_CH$tl, mrip_JX$tl, nboots=1000)$ks.boot.pvalue,
                 ks.boot(mrip_CH$tl, mrip_IR$tl, nboots=1000)$ks.boot.pvalue,
                 ks.boot(mrip_AP$tl, mrip_JX$tl, nboots=1000)$ks.boot.pvalue,
                 ks.boot(mrip_AP$tl, mrip_IR$tl, nboots=1000)$ks.boot.pvalue,
                 ks.boot(mrip_JX$tl, mrip_IR$tl, nboots=1000)$ks.boot.pvalue)

p.adjust(ks_ALL_mrip)
```
ALL
```{r}
ks_ALL <-c(ks.boot(TB$tl, CK$tl, nboots=1000)$ks.boot.pvalue, 
                ks.boot(TB$tl, CH$tl, nboots=1000)$ks.boot.pvalue,
                ks.boot(TB$tl, AP$tl, nboots=1000)$ks.boot.pvalue,
                ks.boot(TB$tl, JX$tl, nboots=1000)$ks.boot.pvalue,
                ks.boot(TB$tl, IR$tl, nboots=1000)$ks.boot.pvalue,
                ks.boot(CK$tl, CH$tl, nboots=1000)$ks.boot.pvalue,
                ks.boot(CK$tl, AP$tl, nboots=1000)$ks.boot.pvalue,
                ks.boot(CK$tl, JX$tl, nboots=1000)$ks.boot.pvalue,
                ks.boot(CK$tl, IR$tl, nboots=1000)$ks.boot.pvalue,
                ks.boot(CH$tl, AP$tl, nboots=1000)$ks.boot.pvalue,
                ks.boot(CH$tl, JX$tl, nboots=1000)$ks.boot.pvalue,
                ks.boot(CH$tl, IR$tl, nboots=1000)$ks.boot.pvalue,
                ks.boot(AP$tl, JX$tl, nboots=1000)$ks.boot.pvalue,
                ks.boot(AP$tl, IR$tl, nboots=1000)$ks.boot.pvalue,
                ks.boot(JX$tl, IR$tl, nboots=1000)$ks.boot.pvalue)

p.adjust(ks_ALL)
```


#### Chi-Square Test
 used to test for differences in length frequencies among different groups (among, times, locations or gears)chi square will generally fail where the contingency table contains zeroes or very small frequencies so best to make the length categories to ensure appropriate sample size # exclude some low and high values so that I can make more appropriate length intervals 

length frequencies of the recreational catch will have changed by year based upon regulatory changes so that
 it is invalid to do yearly comparisons of length frequencies because they were affected by slot limit changes
just compare by bays so combine the data and then make length frequencies
 current is 38 cm to 50 cm  (slot of 15-20)
 started in 2000 but specified above already

MRFSS
```{r}
mrfss_all <- subset(rbind(mrfss_AP, mrfss_TB, mrfss_CH, mrfss_CK, mrfss_JX, mrfss_IR), tl>=30 & tl<= 65) %>% mutate(lcat5=lencat(tl, w=5)) 
mrfss_all$bay <- as.factor(mrfss_all$bay)

(mrfss_lf <- xtabs(~bay+lcat5, data=mrfss_all))
```

multiple comparisons are conducted by isolating pairs of groups, accumulating p-values for each pair and then adjusting the p values for multiple comparisons
```{r warning=FALSE}
ps_mrfss<- c(chisq.test(mrfss_lf[1:2,])$p.value,
chisq.test(mrfss_lf[1:3,])$p.value,
chisq.test(mrfss_lf[1:4,])$p.value,
chisq.test(mrfss_lf[1:5,])$p.value,
chisq.test(mrfss_lf[1:6,])$p.value,
chisq.test(mrfss_lf[2:3,])$p.value,
chisq.test(mrfss_lf[2:4,])$p.value,
chisq.test(mrfss_lf[2:5,])$p.value,
chisq.test(mrfss_lf[2:6,])$p.value,
chisq.test(mrfss_lf[3:4,])$p.value,
chisq.test(mrfss_lf[3:5,])$p.value,
chisq.test(mrfss_lf[3:6,])$p.value,
chisq.test(mrfss_lf[4:5,])$p.value,
chisq.test(mrfss_lf[4:6,])$p.value,
chisq.test(mrfss_lf[5:6,])$p.value)

p.adjust(ps_mrfss)
```
MRIP
```{r}
mrip_all <- subset(rbind(mrip_AP, mrip_TB, mrip_CH, mrip_CK, mrip_JX, mrip_IR), tl>=30 & tl<= 65) %>% mutate(lcat5=lencat(tl, w=5)) 
mrip_all$bay <- as.factor(mrip_all$bay)

(mrip_lf <- xtabs(~bay+lcat5, data=mrip_all))

#multiple comparisons are conducted by isolating pairs of groups, accumulating p-values for each pair and then adjusting the p values for multiple comparisons
ps_mrip<- c(chisq.test(mrip_lf[1:2,])$p.value,
       chisq.test(mrip_lf[1:3,])$p.value,
       chisq.test(mrip_lf[1:4,])$p.value,
       chisq.test(mrip_lf[1:5,])$p.value,
       chisq.test(mrip_lf[1:6,])$p.value,
       chisq.test(mrip_lf[2:3,])$p.value,
       chisq.test(mrip_lf[2:4,])$p.value,
       chisq.test(mrip_lf[2:5,])$p.value,
       chisq.test(mrip_lf[2:6,])$p.value,
       chisq.test(mrip_lf[3:4,])$p.value,
       chisq.test(mrip_lf[3:5,])$p.value,
       chisq.test(mrip_lf[3:6,])$p.value,
       chisq.test(mrip_lf[4:5,])$p.value,
       chisq.test(mrip_lf[4:6,])$p.value,
       chisq.test(mrip_lf[5:6,])$p.value)

p.adjust(ps_mrip)
```


ALL
```{r}
ALL <- subset(rbind(AP, TB, CH, CK, JX, IR), tl>=30 & tl<= 65) %>% mutate(lcat5=lencat(tl, w=5)) 
ALL$bay <- as.factor(ALL$bay)

(ALL_lf <- xtabs(~bay+lcat5, data=ALL))

#multiple comparisons are conducted by isolating pairs of groups, accumulating p-values for each pair and then adjusting the p values for multiplecomparisons

ps_ALL<- c(chisq.test(ALL_lf[1:2,])$p.value, 
            chisq.test(ALL_lf[1:3,])$p.value, 
            chisq.test(ALL_lf[1:4,])$p.value, 
            chisq.test(ALL_lf[1:5,])$p.value, 
            chisq.test(ALL_lf[1:6,])$p.value, 
            chisq.test(ALL_lf[2:3,])$p.value, 
            chisq.test(ALL_lf[2:4,])$p.value, 
            chisq.test(ALL_lf[2:5,])$p.value, 
            chisq.test(ALL_lf[2:6,])$p.value, 
            chisq.test(ALL_lf[3:4,])$p.value, 
            chisq.test(ALL_lf[3:5,])$p.value, 
            chisq.test(ALL_lf[3:6,])$p.value, 
            chisq.test(ALL_lf[4:5,])$p.value, 
            chisq.test(ALL_lf[4:6,])$p.value, 
            chisq.test(ALL_lf[5:6,])$p.value) 

p.adjust(ps_ALL)
```
####ANOVA to test for differences in mean tl between bays

```{r}
aov <- aov(tl ~ bay, data= ALL)
summary(aov)
plot(aov)
# Tukey test
TukeyHSD(aov)
```
```{r include=FALSE}
#MULTIPLOT LENGTH HISTOGRAMS #####
length_AP <- ggplot(AP, aes(x=tl))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-0.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.15), breaks=seq(0,.15, .03))+  ## plotting in percent frequency
  scale_x_continuous(name="Length (cm)", limits=c(30,65), breaks=seq(30,65,5))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24), #changing  colour of x axisaxis.text.y=element_text(colour="black"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24), #changing colour of y acis
        axis.title.x=element_text(size=24),
        axis.title.y=element_text(size=24),
        plot.title=element_text(size=14))+
  annotate("text", x=60, y= .13, label="AP", size=10)

length_CK <- ggplot(CK, aes(x=tl))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-0.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.15), breaks=seq(0,.15, .03))+  ## plotting in percent frequency
  scale_x_continuous(name="Length (cm)", limits=c(30,65), breaks=seq(30,65,5))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24), #changing  colour of x axisaxis.text.y=element_text(colour="black"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24), #changing colour of y acis
        axis.title.x=element_text(size=24),
        axis.title.y=element_text(size=24),
        plot.title=element_text(size=14))+
  annotate("text", x=60, y= .13, label="CK", size=10)

length_TB <- ggplot(TB, aes(x=tl))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-0.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.15), breaks=seq(0,.15, .03))+  ## plotting in percent frequency
  scale_x_continuous(name="Length (cm)", limits=c(30,65), breaks=seq(30,65,5))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24), #changing  colour of x axisaxis.text.y=element_text(colour="black"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24), #changing colour of y acis
        axis.title.x=element_text(size=24),
        axis.title.y=element_text(size=24),
        plot.title=element_text(size=14))+
  annotate("text", x=60, y= .13, label="TB", size=10)

length_CH <- ggplot(CH, aes(x=tl))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-0.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.15), breaks=seq(0,.15, .03))+  ## plotting in percent frequency
  scale_x_continuous(name="Length (cm)", limits=c(30,65), breaks=seq(30,65,5))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24), #changing  colour of x axisaxis.text.y=element_text(colour="black"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24), #changing colour of y acis
        axis.title.x=element_text(size=24),
        axis.title.y=element_text(size=24),
        plot.title=element_text(size=14))+
  annotate("text", x=60, y= .13, label="CH", size=10)

length_JX <- ggplot(JX, aes(x=tl))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-0.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,.15), breaks=seq(0,.15, .03))+  ## plotting in percent frequency
  scale_x_continuous(name="Length (cm)", limits=c(30,65), breaks=seq(30,65,5))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24), #changing  colour of x axisaxis.text.y=element_text(colour="black"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24), #changing colour of y acis
        axis.title.x=element_text(size=24),
        axis.title.y=element_text(size=24),
        plot.title=element_text(size=14))+
  annotate("text", x=60, y= .13, label="JX", size=10)

length_IR <- ggplot(IR, aes(x=tl))+ 
  geom_histogram(aes(y=(..count..)/sum(..count..)), binwidth=1, boundary=-0.5, fill="white", color="black")+    # plotting in percent frequency
  scale_y_continuous(labels=percent_format(), name="Frequency (%)", limits=c(0,0.15), breaks=seq(0,0.15, .03))+  ## plotting in percent frequency
  scale_x_continuous(name="Length (cm)", limits=c(30,65), breaks=seq(30,65,5))+
  theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(), 
        panel.background=element_rect(colour="black",fill="white"), 
        axis.text.x=element_text(colour="black", size=24), #changing  colour of x axisaxis.text.y=element_text(colour="black"), #changing colour of y acis
        axis.text.y=element_text(colour="black", size=24), #changing colour of y acis
        axis.title.x=element_text(size=24),
        axis.title.y=element_text(size=24),
        plot.title=element_text(size=14))+
  annotate("text", x=60, y= .13, label="IR", size=10)
```
### _4.Visualize with CROSSBAR PLOT for mean and standard error_

```{r include=FALSE}
All$bay <- as.factor(All$bay)
All$bay <- ordered(All$bay, levels=c("AP", "CK", "TB", "CH", "JX", "IR"))
levels(All$bay) <-  c("W1_AP", "W2_CK", "W3_TB", "W4_CH", "E1_JX", "E2_IR")
```
function for 95% CI
```{r}
MinMeanSEM196Max <- function(x) {
  v <- c(mean(x) - (sd(x)/sqrt(length(x))*1.96), mean(x), mean(x) + (sd(x)/sqrt(length(x))*1.96))
  names(v) <- c("ymin", "y", "ymax")
  v
}
```

Make plot
```{r}
File <- ("U:/PhD_projectfiles/Figures/rec_length_crossbar.tiff")
#if (file.exists(File)) stop(File, " already exists")
dir.create(dirname(File), showWarnings = FALSE)

tiff(File, units="in", width=5, height=5, res=300)
#scaleFUN <- function(x) sprintf("%.1f", x)
 ggplot(All, aes(bay, tl)) +
  stat_summary(fun.data=MinMeanSEM196Max, geom="crossbar", colour="black") + 
  scale_y_continuous(limits=c(40,48), breaks=seq(40,48, by=1), labels=seq(40,48, by=1))+
  xlab("Estuary")+
  ylab("Total length (cm) ")+
  theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank(), 									
        panel.background=element_rect(fill='white', colour='black'),
        axis.title.y = element_text(colour="black", size=18), # changing font of y axis title
        axis.title.x = element_text(colour="black", size=18),
        axis.text.x=element_text(colour="black", size=12), #changing  colour and font of x axis text
        axis.text.y=element_text(colour="black", size=12)) + 
   annotate("text", label="f", x = 1, y= 42.65) +
   annotate("text", label="f", x = 2, y= 42.55) +
   annotate("text", label="f", x = 5, y= 42.8) +
   annotate("text", label="g", x = 3, y= 43.55) +
   annotate("text", label="h", x = 4, y= 43.3) +
   annotate("text", label="i", x = 6, y= 45.4)
   #changing colour and font of y axis

#plot.title=element_text(size=14), # changing size of plot title)

dev.off()
```
